---
title: "1-10x Breast cancer samples"
author: "Marc Elosua-Bayes"
date: "6/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this R markdown document we are going to look at the QC of breast carcinoma datasets publicly put out by 10X genomics [here](https://support.10xgenomics.com/spatial-gene-expression/datasets/). Specifications of the tissue are the following:

10x Genomics obtained fresh frozen Invasive Ductal Carcinoma breast tissue from BioIVT Asterand.  
The tissue was AJCC/UICC Stage Group IIA, ER positive, PR negative, Her2 positive and annotated with:  

* Ductal carcinoma in situ
* Lobular carcinoma in situ
* Invasive Carcinoma

## Libraries
```{r}
library(Seurat)
library(Spaniel)
library(tidyverse)
library(Matrix)
library(SPOTlight)
source("utils/bin.r")
source("utils/spatial_plot_spaniel.R")
```

## Paths
```{r}
source("misc/paths.R")
dir.create(path = sprintf("%s/%s", an_breast_10x, robj_dir),
           showWarnings = FALSE,
           recursive = TRUE)

dir.create(path = sprintf("%s/%s", an_breast_10x, plt_dir),
           showWarnings = FALSE,
           recursive = TRUE)

```

## Load data
Within this project the data is located at data/breast_visium/section_1 and data/breast_visium/section_2 respectively
```{r}
data_dir <- "data/breast_visium"
sections_dir <- list.files(path = data_dir, full.names = TRUE)

breast_1 <- Seurat::Load10X_Spatial(data.dir = "data/breast_visium/section_1",
                        filename = "filtered_feature_bc_matrix.h5",
                        slice = "breast_1")
breast_1[["slice"]] <- "breast_1"

breast_2 <- Seurat::Load10X_Spatial(data.dir = "data/breast_visium/section_2",
                        filename = "filtered_feature_bc_matrix.h5",
                        slice = "breast_2")
breast_2[["slice"]] <- "breast_2"
```

The first slice has `r nrow(breast_1)` and `r ncol(breast_1)` samples, the second one in turn has `r nrow(breast_2)` and `r ncol(breast_2)` samples.

## Process data
```{r}
breast_1 <- Seurat::SCTransform(object = breast_1, assay = "Spatial")
breast_1 <- Seurat::FindVariableFeatures(breast_1)

breast_2 <- Seurat::SCTransform(object = breast_2, assay = "Spatial")
breast_2 <- Seurat::FindVariableFeatures(breast_2)
```

In order to work with multiple slices in the same Seurat object, we provide the merge function.
```{r}
breast_merged <- merge(breast_1, breast_2)
```


This then enables joint dimensional reduction and clustering on the underlying RNA expression data.
```{r}
Seurat::DefaultAssay(breast_merged) <- "SCT"
Seurat::VariableFeatures(breast_merged) <- c(Seurat::VariableFeatures(breast_1),
                                             Seurat::VariableFeatures(breast_2))
breast_merged <- Seurat::RunPCA(breast_merged,
                                verbose = FALSE)
breast_merged <- Seurat::FindNeighbors(breast_merged,
                                       dims = 1:30)
breast_merged <- Seurat::FindClusters(breast_merged,
                                      verbose = FALSE,
                                      resolution = c(0.1, 0.25, 0.5, 0.8, 1))
breast_merged <- Seurat::RunUMAP(breast_merged,
                                 dims = 1:30)
```

## QC visualization
For the QC we're going to look at the number of RNA counts and the number of genes detected per spot.
```{r}
breast_merged[["percent.mt"]] <- PercentageFeatureSet(breast_merged, pattern = "^MT-")
spt_plt <- Seurat::SpatialFeaturePlot(object = breast_merged,
                                      features = c("nCount_Spatial", "nFeature_Spatial", "percent.mt"),)
spt_plt

ft_plt <- Seurat::VlnPlot(object = breast_merged, 
                          features = c("nCount_Spatial", "nFeature_Spatial", "percent.mt"),
                          group.by = "slice")
ft_plt

SPOTlight::plot_image(img_path = "data/breast_visium/section_1/spatial/tissue_lowres_image.png")
SPOTlight::plot_image(img_path = "data/breast_visium/section_2/spatial/tissue_lowres_image.png")
```

Both slices seem to be of good quality and similar between them which makes sense since they are from the same biopsy.

## Clustering Visualization
```{r}
Seurat::DimPlot(object = breast_merged,
                group.by = c("SCT_snn_res.0.1",
                             "slice"),
                label = TRUE)
Seurat::SpatialDimPlot(object = breast_merged,
                       group.by = c("SCT_snn_res.0.1"),
                       label = TRUE) +
  theme(legend.text = element_text(size = 15)) +
  guides(fill = guide_legend(override.aes = list(size = 5)))
```

## Save data
```{r}
Seurat::Idents(breast_merged) <- breast_merged$SCT_snn_res.0.1
saveRDS(object = breast_merged,
        file = sprintf("%s/%s/breast_merged_processed.RDS", an_breast_10x, robj_dir))
```



