---
title: "2-10x breast GO enrichment"
author: "Marc Elosua-Bayes"
date: "6/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this R markdown document we are going to carry out Gene marker and Gene Ontology enrichment analysis.

## Libraries
```{r}
library(Seurat)
library(Spaniel)
library(tidyverse)
library(Matrix)
library(SPOTlight)
source("utils/bin.r")
source("utils/spatial_plot_spaniel.R")
```

## Paths
```{r}
source("misc/paths.R")
dir.create(path = sprintf("%s/%s", an_breast_10x, robj_dir),
           showWarnings = FALSE,
           recursive = TRUE)

dir.create(path = sprintf("%s/%s", an_breast_10x, plt_dir),
           showWarnings = FALSE,
           recursive = TRUE)

```

## Load data
Data loaded here comes from 1-10x_breast_QC.Rmd and 3-10x_breast_immune_reference.Rmd
```{r}
breast_merged <- readRDS(file = sprintf("%s/%s/breast_merged_processed.RDS", an_breast_10x, robj_dir))
decon_mtrx_ls <- readRDS(file = sprintf("%s/%s/decon_mtrx_breast_cancer_10x.RDS", an_breast_10x, robj_dir))
```

## Analysis
Start by getting the marker genes for the clusters
```{r}
Seurat::Idents(breast_merged) <- breast_merged$SCT_snn_res.0.1
st_markers <- Seurat::FindAllMarkers(object = breast_merged,
                       assay = "SCT",
                       slot = "data",
                       only.pos = TRUE)
st_markers %>% count(cluster)
saveRDS(object = st_markers,
        file = sprintf("%s/%s/markers_breast_10x_res.0.1.RDS", an_breast_10x, robj_dir))
```

Filter top genes
```{r}
pull_col <- function(.x) {
  return(.x %>% pull(var = "gene"))
}

marker_ls <- st_markers %>% 
  dplyr::filter(p_val_adj < 0.01) %>%
  dplyr::group_by(cluster) %>% 
  dplyr::group_split() %>% 
  purrr::map(.f = pull_col)

```

### GO term enrichment analysis
```{r eval = FALSE}
library(org.Hs.eg.db)
library(GOstats)

univ <- stringr::str_split(string = rownames(breast_merged@assays$Spatial@counts),
                           pattern = " ",
                           simplify = TRUE)[, 1]

DE_df1 <- lapply(seq_len(length(marker_ls)), function(i) {
  # gene_set <- convert_symb_entrez(gene_vec = stringr::str_to_upper(markers_ln1_ls[[i]]))
  # gene_universe <- convert_symb_entrez(gene_vec = stringr::str_to_upper(rownames(ln_1)))
  print(i)
  go_clust <- gene_enrichment_GO(gene_de = stringr::str_to_upper(marker_ls[[i]]),
                     gene_universe = univ) %>% 
    summary(.) %>% 
    dplyr::mutate(cluster = i)
  
  return(go_clust)
}) %>% 
  dplyr::bind_rows()

saveRDS(object = DE_df1, file = sprintf("%s/%s/go_enrichment_breast_10x_res.0.1.RDS", an_breast_10x, robj_dir))
```


```{r}
DE_df1 <- readRDS(file = sprintf("%s/%s/go_enrichment_breast_10x_res.0.1.RDS", an_breast_10x, robj_dir))
```

#### Visualization
For visualization purposses we are going to check GO terms at varying levels of specificities.

```{r}
DE_specific <- DE_df1 %>%
  dplyr::filter(Size <= 50 & Pvalue < 0.01 & Count >= 3)

DE_mid <- DE_df1 %>%
  dplyr::filter(Size <= 300 & Size >= 30 & Pvalue < 0.01 & Count >= 3)

DE_general <- DE_df1 %>%
  dplyr::filter(Size > 300 & Pvalue < 0.01 & Count >= 3)
```

```{r}
GO_visualization <- function(ds) {
  plt_ls <- lapply(unique(ds$cluster), function(i) {
    tmp_plt <- ds %>%
      dplyr::filter(cluster == i) %>%
      dplyr::arrange(desc(OddsRatio)) %>%
      head(20) %>% 
      ggplot(.) +
        geom_point(aes(x = OddsRatio,
                       y = reorder(Term, OddsRatio),
                       size = -Pvalue,
                       color = Pvalue)) +
        labs(title = sprintf("Cluster %s", i - 1)) +
        scale_color_gradient(low = "green",
                             high = "red") +
      theme_classic()
    return(tmp_plt)
  })
  return(plt_ls)
}
```

Specific
```{r}
GO_visualization(ds = DE_specific) %>%
  ggpubr::ggexport(plotlist = .,
                   filename = sprintf("%s/%s/go_enrich_breast_10x_res.0.1_specific.pdf",
                                      an_breast_10x, plt_dir),
                   width = 12)
```

Middle
```{r}
GO_visualization(ds = DE_mid) %>%
  ggpubr::ggexport(plotlist = .,
                   filename = sprintf("%s/%s/go_enrich_breast_10x_res.0.1_mid.pdf",
                                      an_breast_10x, plt_dir),
                   width = 12)
```

General
```{r}
GO_visualization(ds = DE_general) %>%
  ggpubr::ggexport(plotlist = .,
                   filename = sprintf("%s/%s/go_enrich_breast_10x_res.0.1_general.pdf",
                                      an_breast_10x, plt_dir),
                   width = 12)
```

Look at estrogen, progesterone and HER2 receptor genes
```{r}
Seurat::SpatialFeaturePlot(object = breast_merged,
                           features = c("ESR1", # Estrogen receptor
                                        "PGR", # Progesterone receptor
                                        "ERBB2"), # HER2 positive
                           alpha = c(0, 1))


Seurat::SpatialDimPlot(object = breast_merged,
                       group.by = "seurat_clusters")

```

