---
title: "3-10x_breast_immune_reference"
author: "Marc Elosua-Bayes"
date: "6/12/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
In this R markdown document we will map immune cells onto the breast cancer tissue. 


```{r}
library(Seurat)
# library(Spaniel)
library(tidyverse)
library(Matrix)
library(SPOTlight)
source("utils/bin.r")
source("utils/spatial_plot_spaniel.R")
```

## Paths
```{r}
source("misc/paths.R")
dir.create(path = sprintf("%s/%s", an_breast_10x, robj_dir),
           showWarnings = FALSE,
           recursive = TRUE)

dir.create(path = sprintf("%s/%s", an_breast_10x, plt_dir),
           showWarnings = FALSE,
           recursive = TRUE)
```

## Parameters
```{r}
trn <- "melanoma"
cl_n <- 100
hvg <- 3000
ntop <- NULL
transf <- "uv"
method <- "nsNMF"
min_cont <- 0
clust_vr <- "new_cell_types"

if (is.null(ntop)) {
  spotlight_id <- sprintf("trn-%s_cln-%s_hvg-%s_ntop-NULL_transf-%s_method-%s_mincont-%s",
                          trn, cl_n, hvg, transf, method, min_cont)
} else {
  spotlight_id <- sprintf("trn-%s_cln-%s_hvg-%s_ntop-%s_transf-%s_method-%s_mincont-%s",
                          trn, cl_n, hvg, ntop, transf, method, min_cont)
}

ct_interest <- c("Plasma B cells", "Regulatory T cells", "T helper cells",
                 "Proliferative T cells", "Pre-exhausted CD8 T cells", "Cytotoxic CD8 T cells",
                 "NK", "SPP1 TAMs", "M2 TAMs")
```

## Load data
Breast cancer data loaded here comes from 1-10x_breast_QC.Rmd
```{r}
### Spatial breast cancer
breast_merged <- readRDS(file = sprintf("%s/%s/breast_merged_processed.RDS",
                                        an_breast_10x, robj_dir))

### Immune reference atlas
if (trn == "full") {
  ica_se <- readRDS("data/immune_reference/atlas_250_specific_cell_type.rds")
} else if (trn == "breast") {
  ica_se <- readRDS("data/immune_reference/atlas_complete_annotation_breast.rds")
} else if (trn == "melanoma") {
  ica_se <- readRDS("data/immune_reference/atlas_complete_annotation_melanoma.rds")
}

# ica_se <- ica_se[, !ica_se$specific_cell_type %in% c("MAST")]
```

Create a name/color dataframe
```{r}
# cell_types <- sort(unique(as.character(ica_se@meta.data[, clust_vr])))
source("misc/col_df_scrpt.R")
```

Change variable names to remove non-standard characters
```{r}
ica_se[["specific_cell_type_mod"]] <- gsub(pattern = "[[:punct:]]|[[:blank:]]", ".",
                               x = as.character(ica_se@meta.data[, clust_vr]), 
                               perl = TRUE)
```

Select 250 cells per cell type
```{r eval = FALSE }
library(dplyr)
n <- 250
keep_id <- ica_se@meta.data %>%
  tibble::rownames_to_column("barcode") %>% 
  dplyr::group_by(specific_cell_type_mod) %>%
  dplyr::sample_n(if(n() < n) n() else n) %>% 
  dplyr::distinct() %>%
  dplyr::pull("barcode")

ica_se <- ica_se[, keep_id]
```

Next we are going to process the seurat object. Since we are working with data from multiple sources and we need to have the data normalized using unit variance we will run SCTransform. We regress the effect of the source while scaling but not centering the data. This way we remove the source batch, perform unit variance scaling and keep it positive by not centering it around 0.
```{r}
Seurat::Idents(ica_se) <- ica_se@meta.data[, "specific_cell_type_mod"]

if (trn == "full") {
  # ica_se <- Seurat::SCTransform(ica_se,
  #                               # Regress out the effect of the study/protocol
  #                               vars.to.regress = "source",
  #                               assay = "RNA",
  #                               # Scale data to unit variance
  #                               do.scale = TRUE,
  #                               # Do NOT center around 0
  #                               do.center = FALSE)
  # saveRDS(object = ica_se,
  #       file = sprintf("%s/%s/ica_se_full_processed.RDS",
  #                      an_breast_10x, robj_dir))
  
  ica_se <- readRDS(file = sprintf("%s/%s/ica_se_full_processed.RDS",
                       an_breast_10x, robj_dir))

} else if (trn == "breast") {
  # ica_se <- Seurat::SCTransform(ica_se,
  #                               assay = "RNA",
  #                               # Scale data to unit variance
  #                               do.scale = TRUE,
  #                               # Do NOT center around 0
  #                               do.center = FALSE)
  # saveRDS(object = ica_se,
  #         file = sprintf("%s/%s/ica_se_breast_processed.RDS",
  #                        an_breast_10x, robj_dir))
  # 
  ica_se <- readRDS(file = sprintf("%s/%s/ica_se_breast_processed.RDS",
                         an_breast_10x, robj_dir))
} else if (trn == "melanoma") {
  # ica_se <- Seurat::SCTransform(ica_se,
  #                             assay = "RNA",
  #                             # Scale data to unit variance
  #                             do.scale = TRUE,
  #                             # Do NOT center around 0
  #                             do.center = FALSE,
  #                             ncells = 5000)
  # saveRDS(object = ica_se,
  #         file = "data/immune_reference/ica_se_melanoma_processed.RDS")
  ica_se <- readRDS(file = "data/immune_reference/ica_se_melanoma_processed.RDS")

}
```

Immune cell marker genes
```{r eval = FALSE}
# ica_se <- Seurat::SCTransform(object = ica_se, assay = "RNA")
ica_markers <- Seurat::FindAllMarkers(object = ica_se,
                       assay = "SCT",
                       slot = "data",
                       only.pos = TRUE,
                       logfc.threshold = 0,
                       min.pct = 0,
                       max.cells.per.ident = 250)

if (trn == "full") {
  saveRDS(object = ica_markers,
        file = "data/immune_reference/ica_markers_all.RDS")
} else if (trn == "breast") {
  saveRDS(object = ica_markers,
        file = "data/immune_reference/ica_markers_breast.RDS")
} else if (trn == "melanoma") {
  saveRDS(object = ica_markers,
        file = "data/immune_reference/ica_markers_melanoma.RDS")
}
```

Check how many unique genes per cluster there are
```{r}
# ica_markers <- readRDS(file = "data/immune_reference/ica_markers_all.RDS")
# ica_markers <- readRDS(file = "data/immune_reference/ica_markers_all_reg-out-source.pdf")
# ica_markers <- readRDS(file = "data/immune_reference/ica_markers_all_latent.RDS")
# ica_markers <- readRDS(file = "data/immune_reference/ica_pdac_markers_all.RDS")

if (trn == "full") {
  ica_markers <- readRDS(file = "data/immune_reference/ica_markers_all.RDS")
} else if (trn == "breast") {
  ica_markers <- readRDS(file = "data/immune_reference/ica_markers_breast.RDS")
} else if (trn == "melanoma") {
  ica_markers <- readRDS(file = "data/immune_reference/ica_markers_melanoma.RDS")
}

# ica_markers <- ica_markers %>%
#   filter(avg_logFC > 0.5 & pct.1 > 0.25)


# Select unique markers from each cluster, if there are common markers between clusters lda model gets confused and classifies very different clusters as belonging to the same topic just because the seeding induced it!
cluster_markers_uniq <- lapply(unique(ica_markers$cluster), function(clust) {
  ls1 <- ica_markers[ica_markers$cluster == clust, "gene"]
  ls2 <- ica_markers[ica_markers$cluster != clust, "gene"]
  ls1_unique <- ls1[! ls1 %in% ls2]

  return(ica_markers[ica_markers$cluster == clust & ica_markers$gene %in% ls1_unique, ])
}) %>%
  dplyr::bind_rows()

ica_markers %>% 
  dplyr::count(cluster) %>% 
  dplyr::left_join(cluster_markers_uniq %>% dplyr::count(cluster, name = "n_unique"))
```

Here we want ot check if the gene markers obtained using UV and no scaling are the same as if we use scaling and no UV
```{r eval = FALSE}
ica_markers_uv <- readRDS(file = "data/immune_reference/ica_markers_all.RDS")

markers_uv_ls <- lapply(unique(ica_markers_uv$cluster), function(clust) {
  ica_markers_uv[ica_markers_uv$cluster == clust, "gene"]
})
names(markers_uv_ls) <- unique(ica_markers_uv$cluster)

  
ica_markers <- readRDS(file = "data/immune_reference/ica_markers_all.RDS")

markers_ls <- lapply(unique(ica_markers$cluster), function(clust) {
  ica_markers[ica_markers$cluster == clust, "gene"]
})
names(markers_ls) <- unique(ica_markers$cluster)

df <- lapply(names(markers_ls), function(ct) {
  norm_uv <- sum(markers_ls[[ct]] %in% markers_uv_ls[[ct]])
  uv_norm <- sum(markers_uv_ls[[ct]] %in% markers_ls[[ct]])
  total_norm <- length(markers_ls[[ct]])
  total_uv <- length(markers_uv_ls[[ct]])
  
  data.frame(norm_uv, uv_norm, total_norm, total_uv)
}) %>% bind_rows()

```

Lastly we need to compute UV normalization of the spatial data so that it applys correctly for all.
In this case we are not correcting for any batch since there is none in the spatial data.
to SPOTlightm since we are passing the argument trasnf = raw, we are going to pass directly the normalized SCT$data matrix.
```{r}
breast_merged <- Seurat::SCTransform(breast_merged,
                              assay = "Spatial",
                              # Scale data to unit variance
                              do.scale = TRUE,
                              # Do NOT center around 0
                              do.center = FALSE)
```

## Deconvolution
Run deconvolution using the previously uv normalized and source-adjusted SCT-data expression matrix.
```{r eval = FALSE}
decon_mtrx_ls <- SPOTlight::spotlight_deconvolution(
  se_sc = ica_se,
  counts_spatial = breast_merged@assays$SCT@data,
  clust_vr = "specific_cell_type_mod",
  cluster_markers = ica_markers,
  cl_n = cl_n,
  hvg = hvg,
  ntop = ntop,
  transf = "raw", # Set to raw 
  method = method,
  min_cont = min_cont,
  assay = "SCT",
  slot = "data")

# saveRDS(object = decon_mtrx_ls,
#         file = sprintf("%s/%s/decon_mtrx_breast_cancer_10x_atlas_%s_reg.RDS",
#                        an_breast_10x, robj_dir, spotlight_id))
# 
# saveRDS(object = decon_mtrx_ls,
#         file = sprintf("%s/%s/decon_mtrx_breast_cancer_10x_atlas_%s_latent.RDS",
#                        an_breast_10x, robj_dir, spotlight_id))

saveRDS(object = decon_mtrx_ls,
        file = sprintf("%s/%s/decon_mtrx_breast_cancer_10x_atlas_%s.RDS",
                       an_breast_10x, robj_dir, spotlight_id))
```

Add deconvolution matrix to Seurat object metadata
```{r}
decon_mtrx_ls <- readRDS(file = sprintf("%s/%s/decon_mtrx_TICA_breast_%s.RDS",
                       an_breast_10x, robj_dir, spotlight_id))

# decon_mtrx_ls <- readRDS(file = sprintf("%s/%s/decon_mtrx_breast_cancer_10x_atlas_%s.RDS",
#                                         an_breast_10x, robj_dir, spotlight_id))
# decon_mtrx_ls <- readRDS(file = sprintf("%s/%s/decon_mtrx_breast_cancer_10x_pdac_atlas.RDS", an_breast_10x, robj_dir))
# decon_mtrx_ls <- readRDS(file = sprintf("%s/%s/decon_mtrx_breast_cancer_10x_atlas_%s_reg.RDS",
#                        an_breast_10x, robj_dir, spotlight_id))
# 
# decon_mtrx_ls <- readRDS(file = sprintf("%s/%s/decon_mtrx_breast_cancer_10x_atlas_%s_latent.RDS",
#                        an_breast_10x, robj_dir, spotlight_id))

decon_mtrx <- decon_mtrx_ls[[2]]
decon_mtrx <- decon_mtrx[, colnames(decon_mtrx) != "res_ss"]

# Set as 0 cell types predicted to be under 0.1 % of the spot
decon_mtrx[decon_mtrx < 0.001] <- 0
```

Change names to original ones and reorder according to Paula
```{r}
new_colnames <- data.frame(ct_name = colnames(decon_mtrx), stringsAsFactors = FALSE) %>%
  dplyr::left_join(col_df, by = "ct_name") %>%
  dplyr::pull(plt_name)

colnames(decon_mtrx) <- new_colnames

paula_order[! paula_order %in% colnames(decon_mtrx)]
decon_mtrx <- decon_mtrx[, paula_order]
```

Add deconvolution matrix to Seurat object metadata
```{r}
breast_merged@meta.data <- cbind(breast_merged@meta.data, decon_mtrx)
```

### Visualization
Before we start we take a look at the topic profiles
```{r}
# Extract coefficient matrix
h <- NMF::coef(decon_mtrx_ls[[1]][[1]])

# Extract coefficient labels
train_labs <- data.frame(ct_name = decon_mtrx_ls[[1]][[2]]) %>%
  dplyr::left_join(col_df, by = "ct_name") %>%
  pull(plt_name)

rownames(h) <- paste("Topic", 1:nrow(h), sep = " ")
profile_plt <- dot_plot_profiles_fun(h = h,
                                 train_cell_clust = train_labs,
                                 clust_vr = "specific_cell_type_mod")
profile_plt[[2]]
profile_plt[[1]]

cowplot::save_plot(filename = sprintf("%s/%s/all_ct_profiles_%s.svg",
                                      an_breast_10x, plt_dir, spotlight_id),
                   plot = profile_plt[[1]],
                   base_height = 30,
                   base_width = 30)

cowplot::save_plot(filename = sprintf("%s/%s/ct_profiles_%s.svg",
                                      an_breast_10x, plt_dir, spotlight_id),
                   plot = profile_plt[[2]] + 
                     theme(axis.title = element_text(size = 18)),
                   base_height = 15,
                   base_width = 15)
```

We will start by looking at the location of each cell type
```{r}
cell_types <- colnames(decon_mtrx)[! colnames(decon_mtrx) %in% "res_ss"]

lapply(seq_len(length(unique(breast_merged$slice))), function(i) {
  slice_n <- unique(breast_merged$slice)[[i]]
  st_se <- breast_merged[, breast_merged$slice == slice_n]
  
  ct_plt_ls <- lapply(cell_types, function(ct) {
    tmp_plt <-Seurat::SpatialFeaturePlot(object = st_se,
                               features = ct,
                               alpha = c(0, 1))
    
    if (sum(st_se@meta.data[, ct]) == 0) {
      tmp_plt <- tmp_plt[[i]] + scale_alpha(range = c(0,0))
    } else {
      tmp_plt <- tmp_plt[[i]] + scale_alpha(range = c(0, 1))
    }
    
    tmp_plt <- tmp_plt +
      theme(
        legend.title = element_blank()
        ) +
      labs(title = ct) +
      scale_fill_gradientn(
        colors = heat.colors(10, rev = TRUE),
        limits = c(0, 1))
      
    # def_plt <- join_seurat_spatial(se_obj = breast_merged,
    #                                grp = "slice",
    #                                plt = tmp_plt,
    #                                feat = ct)
  
  return(tmp_plt)
  })

  cowplot::plot_grid(plotlist = ct_plt_ls,
                     axis = "trbl",
                     align = "hv",
                     nrow = 5,
                     ncol = 5) %>%
    cowplot::save_plot(filename = sprintf("~/Desktop/breast_10x_immune_reference_arrangement_breast-%s.svg",
                                          i),
                       plot = .,
                       base_height = 25,
                       base_width = 25)
      # cowplot::save_plot(filename = sprintf("%s/%s/breast_10x_immune_reference_arrangement_breast-%s.svg",
      #                                     an_breast_10x, plt_dir, i),
      #                  plot = .,
      #                  base_height = 25,
      #                  base_width = 25)

})
```

Next we will only plot the location of the cell types of interest for the main plot
```{r}
# i <- unique(breast_merged$slice)[1]
# ct <- cell_types[[1]]
lapply(seq_len(length(unique(breast_merged$slice))), function(i) {
  print(i)
  slice_n <- unique(breast_merged$slice)[[i]]
  st_se <- breast_merged[, breast_merged$slice == slice_n]
  
  ct_plt_ls <- lapply(ct_interest, function(ct) {
    print(ct)
    tmp_plt <-Seurat::SpatialFeaturePlot(object = st_se,
                               features = ct,
                               alpha = c(0, 1))
    
    if (sum(st_se@meta.data[, ct]) == 0) {
      tmp_plt <- tmp_plt[[i]] + scale_alpha(range = c(0,0))
    } else {
      tmp_plt <- tmp_plt[[i]] +
        scale_fill_gradientn(
          colors = heat.colors(10, rev = TRUE),
          limits = c(0, max(st_se@meta.data[, ct]) + 0.05))
        # scale_alpha(range = c(0, max(st_se@meta.data[, ct]) + 0.05))
    }
    
    tmp_plt <- tmp_plt +
      labs(title = ct) +
      theme(
        plot.title = element_text(size = 20, face = "bold"),
        legend.title = element_blank())
    # def_plt <- join_seurat_spatial(se_obj = breast_merged,
    #                                grp = "slice",
    #                                plt = tmp_plt,
    #                                feat = ct)
  
  return(tmp_plt)
  })

  cowplot::plot_grid(plotlist = ct_plt_ls,
                     axis = "trbl",
                     align = "hv",
                     nrow = 3,
                     ncol = 3) %>%
    cowplot::save_plot(filename = sprintf("%s/%s/breast_10x_immune_reference_arrangement_breast-%s_interest.svg",
                                          an_breast_10x, plt_dir, i),
                       plot = .,
                       base_height = 18,
                       base_width = 15)
})
```

Then we will plot the spatial-scatterpie for both slices to get a gist of what is going on
```{r}
spsct_plt1 <- SPOTlight::spatial_scatterpie(se_obj = breast_merged[, breast_merged$slice == "breast_1"],
                              cell_types_all = cell_types,
                              img_path = "data/breast_visium/section_1/spatial/tissue_lowres_image.png",
                              pie_scale = 0.4,
                              slice = "breast_1") +
              scale_fill_manual(values = col_df[col_df$plt_name %in% cell_types, "ct_col"],
                                breaks = cell_types) +
              guides(fill=guide_legend(ncol = 1))

cowplot::save_plot(filename = sprintf("%s/%s/breast1_10x_spatial_scatterpie.pdf", an_breast_10x, plt_dir),
                   plot = spsct_plt1,
                   base_width = 12,
                   base_height = 9)

spsct_plt2 <- SPOTlight::spatial_scatterpie(se_obj = breast_merged[, breast_merged$slice == "breast_2"],
                              cell_types_all = cell_types,
                              img_path = "data/breast_visium/section_1/spatial/tissue_lowres_image.png",
                              pie_scale = 0.4,
                              slice = "breast_2") +
              scale_fill_manual(values = col_df[col_df$plt_name %in% cell_types, "ct_col"],
                                breaks = cell_types)+
              guides(fill=guide_legend(ncol = 1))

cowplot::save_plot(filename = sprintf("%s/%s/breast2_10x_spatial_scatterpie.pdf", an_breast_10x, plt_dir),
                   plot = spsct_plt2,
                   base_width = 12,
                   base_height = 9)
```

We will also plot the scatterpie without the slice image underneath
```{r}
img_dict <- list()
img_dict[["breast_1"]] <- "breast_1"
img_dict[["breast_2"]] <- "breast_2"
lapply(unique(breast_merged$slice), function(i) {
  sct_plt1 <- SPOTlight::scatterpie_plot(se_obj = breast_merged[, breast_merged$slice == i],
                                         cell_types_all = paula_order,
                                         pie_scale = 0.7,
                                         slice = img_dict[[i]]) +
            scale_fill_manual(values = col_df[col_df$plt_name %in% paula_order, "ct_col"],
                              breaks = paula_order) +
            coord_fixed(ratio = 1) +
            guides(fill = guide_legend(ncol = 1))

  cowplot::save_plot(filename = sprintf("%s/%s/breast_%s_10x_scatterpie.svg",
                                        an_breast_10x, plt_dir, i),
                     plot = sct_plt1,
                     base_width = 12,
                     base_height = 9)
})
```

We can also take a loot at the spatial scatterpie by looking at cell types which are not present throughout the entire tissue.
```{r}
lapply(unique(breast_merged$slice), function(i) {
  # Subset slice
  st_se <- breast_merged[, breast_merged$slice == i]
  
  # Subset cell types from metadata
  metadata_subset <- st_se@meta.data[, paula_order]
  
  # Create masks
  keep_0.9 <- colSums(st_se@meta.data[, paula_order] > 0) < 0.9 * ncol(st_se)
  keep_g0 <- colSums(st_se@meta.data[, paula_order] > 0) > 0
  
  # Select cell types fullfiling the conditions
  ct_var <- colnames(decon_mtrx)[keep_0.9 & keep_g0]

  sct_plt <- SPOTlight::scatterpie_plot(se_obj = st_se,
                                         cell_types_all = ct_var,
                                         pie_scale = 0.4,
                                         slice = img_dict[[i]]) +
            scale_fill_manual(values = col_df[col_df$plt_name %in% ct_var, "ct_col"],
                              breaks = ct_var) +
            labs(fill = "") +
            coord_fixed(ratio = 1) +
            theme(legend.position = "top") +
            guides(fill = guide_legend(nrow = 3))

  cowplot::save_plot(filename = sprintf("%s/%s/breast_10x_scatterpie_variable_subset_%s.svg",
                                        an_breast_10x, plt_dir, i),
                     plot = sct_plt,
                     base_width = 12,
                     base_height = 9)
  
  # cowplot::save_plot(filename = sprintf("~/Downloads/breast_10x_scatterpie_variable_subset_%s.svg",
  #                                       i),
  #                    plot = sct_plt,
  #                    base_width = 12,
  #                    base_height = 9)

})

```

### Gene - Cell correlation
Check assumptions
```{r}
lapply(unique(breast_merged$slice), function(i) {
  st_se <- breast_merged[, breast_merged$slice == i]
  
  lapply(c("Regulatory T cells", "Proliferative T cells"), function(ct) {
    # Shapiro-Wilk normality test for mpg
    print(shapiro.test(st_se@meta.data[, ct]))
    ggpubr::ggqqplot(st_se@meta.data[, ct])
  
  })
  
  lapply(c("ENTPD1", "NT5E", "TGFB1"), function(gene) {
    # Shapiro-Wilk normality test for mpg
    print(shapiro.test(st_se@assays$SCT@data[gene, ]))
    ggpubr::ggqqplot(st_se@assays$SCT@data[gene, ])
  
  })
})
```

Next we want to check if the fibrotic marker TGFB1 with Treg and Tprolif 
```{r}
library(ggpubr)
tmp_plts <- lapply(unique(breast_merged$slice), function(i) {
  st_se <- breast_merged[, breast_merged$slice == i]
  
  metadata <- dplyr::bind_cols(st_se@meta.data,
                               data.frame(t(st_se@assays$SCT@data[c("ENTPD1", "NT5E", "TGFB1"), ])))
  
  cor_plts <- lapply(c("Regulatory T cells", "Proliferative T cells"), function(ct) {
    # tmp_ls <- lapply(c("ENTPD1", "NT5E", "TGFB1"), function(gene) {
    tmp_ls <- lapply(c("TGFB1"), function(gene) {
      
      tmp_plt <- ggpubr::ggscatter(data = metadata,
                        x = gene,
                        y = ct,
                        add = "reg.line") +
         ggpubr::stat_cor(method = "pearson")
      return(tmp_plt)
    })
    
    cowplot::plot_grid(plotlist = tmp_ls, ncol = 1)
  })
  
  tmp_arr <- cowplot::plot_grid(plotlist = cor_plts,
                                nrow = 1,
                                ncol = 2)
  
  # now add the title
  title <- cowplot::ggdraw() +
    cowplot::draw_label(
      i,
      fontface = 'bold',
      x = 0,
      hjust = 0,
      size = 20
    ) +
    ggplot2::theme(
      # add margin on the left of the drawing canvas,
      # so title is aligned with left edge of first plot
      plot.margin = margin(0, 0, 0, 20)
    )
  
  cowplot::plot_grid(
    title, tmp_arr,
    ncol = 1,
    # rel_heights values control vertical title margins
    rel_heights = c(0.1, 1)
  )
}) %>%
  cowplot::plot_grid(plotlist = tmp_plts,
                     nrow = 2)

tmp_plts
```

## Session Info
```{r}
sessionInfo()
```

