---
author: "Marc Elosua-Bayes"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  BiocStyle::html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    df_print: paged
editor_options: 
  chunk_output_type: console
params: 
    sample_id: "Default!"
    clust_vr: "Default!"
title: "`r sprintf('4-10x breast stratification %s', {params$sample_id})`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "100%", fig.align='center', 
                      message = FALSE, warning = FALSE)
options(width = 1200)
```

## Introduction
In this script we are going to stratify the tissue in different ways to assess different immune infiltrations. The pathologist's  annotation of the tissue is the following>

```{r}
library(Seurat)
library(tidyverse)
library(Matrix) 
library(SPOTlight)
# library(svglite)
library(corrplot)
library(ggcorrplot)

source(here::here("utils/bin.r"))
```

## Parameters
```{r}
set.seed(1243)

sample_id <- params$sample_id
# sample_id <- "breast_1"
# sample_id <- "breast_2"
clust_vr <- params$clust_vr
# clust_vr <- "lv2_annot"
# clust_vr <- "lv1_annot"

trn <- "melanoma"
cl_n <- 100
hvg <- 3000
ntop <- NULL
transf <- "uv"
method <- "nsNMF"
min_cont <- 0

if (is.null(ntop)) {
  spotlight_id <- glue::glue("trn-{trn}_cln-{cl_n}_hvg-{hvg}_ntop-NULL_transf-{transf}_method-{method}_mincont-{min_cont}")
} else {
  spotlight_id <- glue::glue("trn-{trn}_cln-{cl_n}_hvg-{hvg}_ntop-{ntop}_transf-{transf}_method-{method}_mincont-{min_cont}")
}
```

Define cell types of interest depending on the annotation level
```{r}
if (clust_vr == "lv2_annot") {
  ct_interest <- c("Plasma.B.cells", "T.regs", "T.helper.Th17",
                 "Proliferation", "CD8.exhausted",
                 "CD8.cytotoxic", "NK", "Macrophages.SPP1", "TAMs.C1QC")
} else if (clust_vr == "lv1_annot") {
  ct_interest <- c("Plasma B cells", "T cells regulatory", "T helper cells",
                 "Proliferation", "CD8 pre-exhausted",
                 "CD8 terminally exhausted", "NK", "Macrophages SPP1", "TAMs C1QC")
}
```

## Paths
```{r}
source(here::here("misc/paths.R"))

"{an_breast_10x}/{robj_dir}" %>%
  glue::glue() %>%
  here::here() %>%
  dir.create(
    path = ,
    showWarnings = FALSE,
    recursive = TRUE)

"{an_breast_10x}/{plt_dir}" %>%
  glue::glue() %>%
  here::here() %>%
  dir.create(
    path = ,
    showWarnings = FALSE,
    recursive = TRUE)
```

## Load data
Breast cancer data loaded here comes from 1-10x_breast_QC.Rmd
```{r}
### Breast cancer
### Spatial breast cancer
se_obj <- "{an_breast_10x}/{robj_dir}/qc_se_{sample_id}.rds" %>%
  glue::glue() %>%
  here::here() %>%
  readRDS(file = .)

### Deconvolution
# decon_mtrx_ls <- readRDS(file = sprintf("%s/%s/decon_mtrx_TICA_breast_%s.RDS",
#                        an_breast_10x, robj_dir, spotlight_id))
decon_mtrx_ls <- "{an_breast_10x}/{robj_dir}/decon_mtrx_breast_cancer_10x_atlas_{sample_id}_{spotlight_id}_{clust_vr}.rds" %>%
  glue::glue() %>%
  here::here() %>%
  readRDS(file = .)
```

Create a name/color dataframe
```{r}
# source(here::here("misc/col_df_scrpt.R"))
# source(here::here("misc/col_df_scrpt2.R"))
col_df <- readRDS(here::here("misc/col_df.rds"))
```

Change names to original ones and reorder according to Paula
```{r}
decon_mtrx <- decon_mtrx_ls[[2]]
decon_mtrx <- decon_mtrx[, colnames(decon_mtrx) != "res_ss"]

# Set as 0 cell types predicted to be under 3 % of the spot
decon_mtrx[decon_mtrx < 0.03] <- 0

new_colnames <- data.frame(ct_name = colnames(decon_mtrx), stringsAsFactors = FALSE) %>%
  dplyr::left_join(col_df, by = "ct_name") %>%
  dplyr::pull(plt_name)

colnames(decon_mtrx) <- new_colnames
```

Add deconvolution matrix to Seurat object metadata
```{r}
se_obj@meta.data <- cbind(se_obj@meta.data, round(decon_mtrx, 3))
```

Convert to dataframe
```{r}
decon_df <- data.frame(decon_mtrx)
colnames(decon_df) <- colnames(decon_mtrx)
decon_df <- decon_df[, which(colnames(decon_df) != "res_ss")]
```

Set paula order sub for subsequent use
```{r}
ct <- colnames(decon_df)[!colnames(decon_df) %in% "res_ss"]
```

## Clustering
```{r}
se_obj <- Seurat::RunPCA(se_obj,
                                verbose = FALSE) %>%
  Seurat::FindNeighbors(., dims = 1:30, verbose = FALSE) %>%
  Seurat::FindClusters(.,
                       verbose = FALSE,
                       resolution = c(0.075, 0.1, 0.25, 0.5, 0.8, 1)) %>%
  Seurat::RunUMAP(., dims = 1:30, verbose = FALSE)
```

## Stratify tissue
```{r}
esr_plt <- Seurat::SpatialFeaturePlot(object = se_obj,
                           features = c("ESR1"), # Estrogen receptor
                           alpha = c(0, 1)) +
  labs(title = "Breast ESR1") +
  theme(plot.title = element_text(size = 20,
                                  hjust = 0.5,
                                  face = "bold"))

pgr_plt <- Seurat::SpatialFeaturePlot(object = se_obj,
                           features = c("PGR"), # Progesterone receptor,
                           alpha = c(0, 1))

her_plt <- Seurat::SpatialFeaturePlot(object = se_obj,
                           features = c("ERBB2"), # HER2 positive
                           alpha = c(0, 1))
ki67_plt <- Seurat::SpatialFeaturePlot(object = se_obj,
                           features = c("MKI67"), # KI67 proliferation
                           alpha = c(0, 1))

if (sample_id == "breast_1") {
  dim_plt <- Seurat::SpatialDimPlot(object = se_obj,
                       group.by = "SCT_snn_res.0.1")
} else if (sample_id == "breast_2") {
  dim_plt <- Seurat::SpatialDimPlot(object = se_obj,
                       group.by = "SCT_snn_res.0.25")
}

esr_plt + pgr_plt + her_plt + ki67_plt + dim_plt
```

#### Markers
TGFB1 is a known fibrotic marker.
```{r}
sp_cl <- Seurat::SpatialDimPlot(object = se_obj,
                                group.by = "SCT_snn_res.0.1")

sp_tmp <- Seurat::SpatialFeaturePlot(object = se_obj,
                           features = "TGFB1",
                           alpha = c(0, 1))

vln_tmp <- Seurat::VlnPlot(object = se_obj,
                         features = "TGFB1",
                         group.by = "SCT_snn_res.0.1",
                         assay = "SCT",
                         slot = "data")

tmp <- sp_cl + sp_tmp + vln_tmp
tmp
"{an_breast_10x}/{plt_dir}/fibrotic_marker_{sample_id}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = ,
    plot = tmp,
    base_height = 5,
    base_width = 15)
```

From here we can determine some correspondance between Estrogen receptor and HER2+ expression. So with Cluster resolution at 0.1 we observe the following correspondance:

* Cluster 2 and 3 show high expression of ESR1
* Cluster 3 and 4 show a high expression of ERBB2 (HER2+)

We are now interested in if there is different immune infiltrations between those regions and the rest. To do se we'll stratify the tissue into those categories.
```{r}
if (sample_id == "breast_1") {
  se_obj[["HER2_ESR1"]] <- factor(dplyr::case_when(
                        se_obj$SCT_snn_res.0.1 %in% c(3) ~ "HER2+/ESR1+",
                        se_obj$SCT_snn_res.0.1 %in% c(2) ~ "HER2-/ESR1+",
                        se_obj$SCT_snn_res.0.1 %in% c(4) ~ "HER2+/ESR1-",
                        se_obj$SCT_snn_res.0.1 %in% c(0) ~ "Fibrotic",
                        TRUE ~ "HER2-/ESR1-"), 
                        levels = c("Fibrotic", "HER2+/ESR1+",
                                   "HER2+/ESR1-", "HER2-/ESR1+",
                                   "HER2-/ESR1-"))

} else if (sample_id == "breast_2") {
  se_obj[["HER2_ESR1"]] <- factor(dplyr::case_when(
                        se_obj$SCT_snn_res.0.25 %in% c(4) ~ "HER2+/ESR1+",
                        se_obj$SCT_snn_res.0.25 %in% c(3) ~ "HER2-/ESR1+",
                        se_obj$SCT_snn_res.0.25 %in% c(5) ~ "HER2+/ESR1-",
                        se_obj$SCT_snn_res.0.25 %in% c(0, 1) ~ "Fibrotic",
                        TRUE ~ "HER2-/ESR1-"), 
                        levels = c("Fibrotic", "HER2+/ESR1+",
                                   "HER2+/ESR1-", "HER2-/ESR1+",
                                   "HER2-/ESR1-"))
}
```

```{r}
strat_plt <- Seurat::SpatialDimPlot(object = se_obj,
                       group.by = "HER2_ESR1")

tmp_plt <- cowplot::plot_grid(plotlist = list(esr_plt +
                                                labs(title = "ESR1") +
                                                theme(plot.title = element_text(size = 20,
                                                                                hjust = 0.5,
                                                                                face = "bold"),
                                                      legend.title = element_blank()),
                                              her_plt +
                                                labs(title = "ERBB2") +
                                                theme(plot.title = element_text(size = 20,
                                                                                hjust = 0.5,
                                                                                face = "bold"),
                                                      legend.title = element_blank()),
                                              # pgr_plt[[i]] +
                                              #   labs(title = "PGR") +
                                              #   theme(plot.title = element_text(size = 20,
                                              #                                   hjust = 0.5,
                                              #                                   face = "bold"),
                                              #         legend.title = element_blank()),
                                              strat_plt +
                                                labs(title = "") +
                                                scale_fill_brewer(palette = "Set1") +
                                                theme(
                                                  legend.position="top",
                                                  legend.title = element_blank()) +
                                                guides(fill = guide_legend(override.aes = list(size = 5),
                                                                           nrow = 3))
                                                      ),
                              nrow = 3,
                              align = "hv",
                              axis = "trbl")

# cowplot::save_plot(filename = sprintf("%s/%s/breast_gene_expression_%s.pdf",
#                                       an_breast_10x, plt_dir, i),
#                    plot = tmp_plt,
#                    base_height = 9,
#                    base_width = 15)

# cowplot::save_plot(filename = sprintf("%s/%s/breast_gene_expression_%s.svg",
#                                       an_breast_10x, plt_dir, i),
#                    plot = tmp_plt,
#                    base_height = 9,
#                    base_width = 15)
tmp_plt

"{an_breast_10x}/{plt_dir}/breast_gene_expression_{sample_id}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = tmp_plt,
    base_height = 15,
    base_width = 4)
```

Extract metadata from Seurat object and join it with the deconvolution
```{r}
metadata <- se_obj@meta.data
```

Format the data into long format
```{r}
metadata_long <- metadata %>% 
  tidyr::pivot_longer(cols = c("HER2_ESR1"),
                      names_to = "stratification_id",
                      values_to = "stratification_val") %>%
  tidyr::pivot_longer(cols = all_of(ct), names_to = "immune_key", values_to = "immune_val") %>%
  dplyr::left_join(col_df, by = c("immune_key" = "ct_name")) %>%
  dplyr::mutate(immune_val = dplyr::if_else(immune_val > 0.001, immune_val, 0))

metadata_long %>% dplyr::count(immune_key)
metadata_long %>% filter(immune_key == "B cells") %>% select(immune_key, immune_val)
```

### HER2-ESR1
Box plot of cell type proportion between stratified regions showing the unadjusted ANOVA Pvalue
```{r}
keep_ct <- metadata_long %>%
  dplyr::group_by(immune_key) %>%
  dplyr::summarise(prop_sum = sum(immune_val)) %>% 
  dplyr::filter(prop_sum > 0) %>%
  dplyr::pull(immune_key)

bplt_her2_esr1 <- metadata_long %>%
  dplyr::filter(stratification_id == "HER2_ESR1") %>%
  dplyr::filter(immune_key %in% keep_ct) %>%
  dplyr::mutate(
    immune_key = stringr::str_wrap(string = immune_key,
                                   width = 30)) %>%
  dplyr::mutate(stratification_val = factor(stratification_val, 
                                            levels = c("Fibrotic", "HER2+/ESR1+",
                                                       "HER2+/ESR1-", "HER2-/ESR1+",
                                                       "HER2-/ESR1-"))) %>%
  # dplyr::filter(! plt_name %in% c("CD8 EM-like", "CD4 naive-like")) %>%
  ggpubr::ggboxplot(data = .,
                    x = "stratification_val",
                    y = "immune_val",
                    facet.by = "immune_key",
                    color = "stratification_val",
                    fill = "stratification_val",
                    add = "jitter",
                    scales = "free",
                    repel = TRUE,
                    outlier.shape = NA,
                    alpha = 0.6,
                    palette = "Set1") +
  theme(
    strip.text = element_text(size = 18, face = "bold"),
    axis.text.y = element_text(size = 16),
    axis.title.y = element_text(size = 20),
    axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5, hjust = 0.5),
    legend.text = element_text(size = 18),
    legend.title = element_blank(),
    strip.background = element_blank()) +
  labs(y = "Proportion",
       color = "Regions",
       fill = "Regions")
  
bplt_her2_esr1 <- bplt_her2_esr1 +
  ggpubr::stat_compare_means(method = "anova", size = 6) +
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.1)),
    labels = function(x) sprintf("%.2f", x))

"{an_breast_10x}/{plt_dir}/strat_bplot_breast_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = bplt_her2_esr1,
    base_height = 25,
    base_width = 25)
```

Now only doing the boxplots for the cell types of interest for the main figure
```{r}
# https://stackoverflow.com/questions/28436855/change-the-number-of-breaks-using-facet-grid-in-ggplot2
# defining the breaks function, 
# s is the scaling factor (cf. multiplicative expand)
equal_breaks <- function(n = 3, s = 0.05, ...){
  function(x){
    # rescaling
    d <- s * diff(range(x)) / (1 + 2 * s)
    round(seq(min(x) + d, max(x) - d, length = n), 2)
  }
}

# i = unique(metadata_long$slice)[1]
bplt_her2_esr1_int <- metadata_long %>%
  dplyr::filter(stratification_id == "HER2_ESR1") %>%
  dplyr::filter(immune_key %in% ct_interest) %>%
  dplyr::mutate(immune_key = stringr::str_wrap(string = immune_key,
                                               width = 30)) %>%
  dplyr::mutate(stratification_val = factor(stratification_val, 
                                            levels = c("Fibrotic", "HER2+/ESR1+",
                                                       "HER2+/ESR1-", "HER2-/ESR1+",
                                                       "HER2-/ESR1-"))) %>%
  # dplyr::filter(! plt_name %in% c("CD8 EM-like", "CD4 naive-like")) %>%
  ggpubr::ggboxplot(data = .,
                    x = "stratification_val",
                    y = "immune_val",
                    facet.by = "immune_key",
                    color = "stratification_val",
                    fill = "stratification_val",
                    add = "jitter",
                    scales = "free",
                    repel = TRUE,
                    outlier.shape = NA,
                    alpha = 0.6,
                    palette = "Set1") +
  ggplot2::theme(
    strip.text = ggplot2::element_text(size = 16, face = "bold"),
    axis.text.x = ggplot2::element_blank(),
    axis.text.y = ggplot2::element_text(size = 16, hjust = 1),
    legend.text = ggplot2::element_text(size = 16),
    legend.title = ggplot2::element_text(size = 16, face = "bold"),
    axis.title.y = ggplot2::element_text(size = 16, face = "bold"),
    axis.title.x = ggplot2::element_blank(),
  strip.background = ggplot2::element_blank()) +
  ggplot2::labs(y = "Proportion",
       color = "Regions",
       fill = "Regions") +
  ggplot2::scale_y_continuous(
    # Set exactly 3 breaks
    breaks = equal_breaks(n = 3, s = 0.05),
    # use same s as first expand argument, 
    # second expand argument should be 0
    expand = c(0.05, 0),
    # Remove unnecessary 0 to the right of the decimal
    labels = function(x) sapply(x, FUN = function(i) format(x = i, nsmall = 0)))
  # scale_y_continuous(
  #   limits = c(0, NA),
  #   labels = function(x) sprintf("%.2f", x))
  
bplt_her2_esr1_int +
  ggpubr::stat_compare_means(method = "anova", size = 5) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))

"{an_breast_10x}/{plt_dir}/strat_bplot_breast_{sample_id}_{clust_vr}_interest.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = bplt_her2_esr1_int,
    base_height = 8,
    base_width = 12)
```

```{r eval = FALSE}
vec <- metadata_long %>%
  dplyr::filter(stratification_id == "HER2_ESR1") %>%
  dplyr::pull("stratification_val") %>% 
  unique()

# Define list of pairwise interactions to test
my_comparisons <- tidyr::crossing(vec, vec,.name_repair = "unique") %>% 
  dplyr::filter(vec...1 < vec...2)

y_pos <- metadata_long %>% 
  dplyr::filter(stratification_id == "HER2_ESR1") %>%
  dplyr::group_by(plt_name) %>%
  dplyr::summarise(y.position = max(immune_val))

# T-test annotation table with adjusted pvals and y-position of the labels
anno_df_wilcox_her2_esr1 <- metadata_long %>% 
  dplyr::filter(stratification_id == "HER2_ESR1") %>%
  # dplyr::filter(! plt_name %in% c("CD8 EM-like", "CD4 naive-like")) %>%
  ggpubr::compare_means(data = .,
                        formula = immune_val ~ stratification_val,
                        method = "wilcox.test",
                        group.by = "plt_name",
                        p.adjust.method = "bonferroni",
                        comparisons = my_comparisons) %>% 
    dplyr::left_join(y_pos, by = "plt_name") %>% 
    dplyr::mutate(y.position = if_else(group1 == "Fibrotic" & 
                                       group2 == "HER2-", 
                                     y.position * 0.7, 
                                     if_else(group1 == "Fibrotic" &
                                               group2 == "HER2+", 
                                             y.position * 0.8,
                                             y.position * 0.93)))
bplt_her2_esr1 +
  ggpubr::stat_pvalue_manual(data = anno_df_wilcox_her2_esr1,
                             # label = "p = {p.adj}",
                             label = "p.signif",
                             y.position = "y.position",
                             size = 4,
                             step.increase = 0.2,
                             step.group.by = "group1") 

```

#### Localization Heatmap
Proportion heatmap, Here we look at the proportion of spots within each stratified regions contains a cell type regardless of its proportion.
```{r}
tmp_df <- metadata %>%
  dplyr::mutate(total = 1) %>%
  dplyr::select(all_of(c(ct, "total", "HER2_ESR1"))) %>%
  tidyr::pivot_longer(cols = all_of(ct)) %>%
  dplyr::mutate(value = if_else(value < 0.001, 0, 1)) %>%
  dplyr::group_by(name, HER2_ESR1) %>%
  dplyr::summarise(freq = sum(value) / sum(total))

# Plot heatmap
hm_tmp <- tmp_df %>%
  ggplot(aes(x = HER2_ESR1, 
             y = name, 
             fill= freq)) + 
  geom_tile(color = "lightgrey") +
  geom_text(aes(label = round(freq, 2)), 
            show.legend = FALSE) +
  labs(title = "Breast carcinoma cell-type enrichment by region",
       y = "Cell types", 
       x = "",
       fill = "Proportion") +
  theme_classic() +
  scale_y_discrete(limits = rev(ct),
                   labels = stringr::str_wrap(
                     string = rev(ct),
                     width = 21)) +
  scale_fill_gradient(low = "#FFF5F0",
                      high = "#99000D",
                      guide = "legend",
                      limits = c(0, 1),
                      breaks = seq(0, 1, 0.1)) +
  scale_alpha_continuous(guide = "legend",
                         limits = c(0, 1), 
                         breaks = seq(0, 1, 0.1)) +
  theme(axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 17),
        plot.title = element_text(hjust = 0.5, face = "bold", size = 18),
        axis.title = element_text(size = 15),
        axis.line = element_blank())

hm_tmp

"{an_breast_10x}/{plt_dir}/strat_heatmap_breast_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = hm_tmp,
    base_height = 15,
    base_width = 9)

# Plot heatmap without text
hm_tmp2 <- tmp_df %>%
  ggplot(aes(x = HER2_ESR1, 
             y = name, 
             fill= freq)) + 
  geom_tile(color = "lightgrey") +
  # geom_text(aes(label = round(freq, 2)), 
  #           show.legend = FALSE) +
  labs(title = "Breast carcinoma cell-type enrichment by region",
       y = "Cell types", 
       x = "",
       fill = "Proportion") +
  theme_classic() +
  scale_y_discrete(limits = rev(ct)) +
  scale_fill_gradient(low = "#FFF5F0",
                      high = "#99000D",
                      guide = "legend",
                      limits = c(0, 1),
                      breaks = seq(0, 1, 0.1)) +
  scale_alpha_continuous(guide = "legend",
                         limits = c(0, 1), 
                         breaks = seq(0, 1, 0.1)) +
  theme(axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 17),
        plot.title = element_text(hjust = 0.5, face = "bold", size = 18),
        axis.title = element_text(size = 15),
        axis.line = element_blank())


"{an_breast_10x}/{plt_dir}/strat_heatmap_breast_{sample_id}_{clust_vr}_labelless.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = hm_tmp2,
    base_height = 15,
    base_width = 9)
```

Now heatmap with only cells of interest
```{r eval = FALSE}
tmp_df <- metadata %>%
  dplyr::mutate(total = 1) %>%
  dplyr::select(all_of(c(ct_interest, "total", "HER2_ESR1"))) %>%
  tidyr::pivot_longer(cols = all_of(ct_interest)) %>%
  dplyr::mutate(value = if_else(value < 0.001, 0, 1)) %>%
  dplyr::group_by(name, HER2_ESR1) %>%
  dplyr::summarise(freq = sum(value) / sum(total))

# Plot heatmap without text
hm_tmp_int <- tmp_df %>%
  ggplot(aes(x = HER2_ESR1, 
             y = name, 
             fill= freq)) + 
  geom_tile(color = "lightgrey") +
  # geom_text(aes(label = round(freq, 2)), 
  #           show.legend = FALSE) +
  labs(title = "Breast carcinoma cell-type enrichment by region",
       y = "Cell types", 
       x = "",
       fill = "Proportion") +
  theme_classic() +
  scale_y_discrete(limits = rev(ct_interest),
                   labels = stringr::str_wrap(string = rev(ct_interest),
                                              width = 21)) +
  scale_fill_gradient(low = "#FFF5F0",
                      high = "#99000D",
                      guide = "legend",
                      limits = c(0, 1),
                      breaks = seq(0, 1, 0.1)) +
  scale_alpha_continuous(guide = "legend",
                         limits = c(0, 1), 
                         breaks = seq(0, 1, 0.1)) +
  theme(axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 17),
        plot.title = element_text(hjust = 0.5, face = "bold", size = 18),
        axis.title = element_text(size = 15),
        axis.line = element_blank())

"{an_breast_10x}/{plt_dir}/strat_heatmap_breast_{sample_id}_{clust_vr}_labelless_interest.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = hm_tmp_int,
    base_height = 15,
    base_width = 9)
```


## Cell-Cell correlation plot
By looking at correlations we want to assess if there are cell types which are correlating in space. So when one is present is another one also present?

We will be using `ggcorrplot` to show these correlation plots a bit nicer:
http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2
<!-- http://www.sthda.com/english/wiki/visualize-correlation-matrix-using-correlogram -->

Get correlation matrix between all cell types
```{r}
decon_df <- metadata %>%
  dplyr::select(all_of(ct))

# Remove cell types not predicted to be on the tissue
decon_df <- decon_df[, colSums(decon_df) > 0]
decon_cor <- cor(decon_df)

# Compute correlation P-value
p.mat <- corrplot::cor.mtest(mat = decon_df, conf.level = 0.95)
colnames(decon_cor) <- stringr::str_wrap(string = colnames(decon_cor), width = 30)
rownames(decon_cor) <- stringr::str_wrap(string = rownames(decon_cor), width = 30)


cor_plt <- ggcorrplot::ggcorrplot(corr = decon_cor,
           p.mat = p.mat[[1]],
           hc.order = TRUE,
           type = "full",
           insig = "blank",
           lab = TRUE,
           outline.col = "lightgrey",
           method = "square",
           # colors = c("#4477AA", "white", "#BB4444"))
           colors = c("#6D9EC1", "white", "#E46726"),
           title = "Breast carcinoma cell-cell proportion correlation",
           legend.title = "Correlation\n(Pearson)") +
   theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 15),
    axis.text.x = element_text(angle = 90),
    axis.text = element_text(size = 18, vjust = 0.5))
cor_plt
# cowplot::save_plot(plot = cor_plt,
#                  filename = sprintf("%s/%s/correlation_plot_breast_%s.pdf",
#                      an_breast_10x, plt_dir, i),
#                  base_width = 16,
#                  base_height = 12)

"{an_breast_10x}/{plt_dir}/correlation_plot_breast_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = cor_plt,
    base_height = 16,
    base_width = 12)

# Now without labels
cor_plt2 <- ggcorrplot::ggcorrplot(corr = decon_cor,
           p.mat = p.mat[[1]],
           hc.order = TRUE,
           type = "full",
           insig = "blank",
           lab = FALSE,
           outline.col = "lightgrey",
           method = "square",
           # colors = c("#4477AA", "white", "#BB4444"))
           colors = c("#6D9EC1", "white", "#E46726"),
           title = glue::glue("Breast carcinoma cell-cell proportion correlation\nSample-{sample_id}"),
           legend.title = "Correlation\n(Pearson)") +
  theme(
    plot.title = element_text(size = 25, hjust = 0.5, face = "bold"),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 22),
    axis.text.x = element_text(angle = 90, size = 18, vjust = 0.5),
    axis.text.y = element_text(vjust = 0.5, size = 18))

cor_plt2

"{an_breast_10x}/{plt_dir}/correlation_plot_breast_{sample_id}_{clust_vr}_labelless.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = cor_plt2,
    base_height = 16,
    base_width = 12)
```

### Correlation scatterplots
Select top 16 scatterplots pairs
```{r eval = FALSE}
decon_df <- metadata %>%
  dplyr::select(all_of(ct))
# Remove cell types not predicted to be on the tissue
decon_df <- decon_df[, colSums(decon_df) > 0]
decon_cor <- cor(decon_df)

decon_cor[lower.tri(decon_cor)] <- NA
decon_low <- data.frame(decon_cor)
colnames(decon_low) <- rownames(decon_low)

ct_scatterplot <- decon_low %>%
  tibble::rownames_to_column("ct_1") %>% 
  tidyr::pivot_longer(cols = colnames(decon_cor),
                      names_to ="ct_2",
                      values_to = "cor_val") %>%
  dplyr::filter(ct_1 != ct_2) %>%
  dplyr::arrange(desc(abs(cor_val))) %>%
  head(16) %>%
  dplyr::mutate(ct_12 = sprintf("%s.%s", ct_1, ct_2)) %>%
  dplyr::pull(ct_12)

corr_plts <- lapply(ct_scatterplot, function(i) {
  # separate ct_12
  str_ls <- stringr::str_split(i, "\\.")
  ct1 <-str_ls[[1]][[1]]
  ct2 <-str_ls[[1]][[2]]
  
  ggplot(decon_df,
         aes(x = decon_df[, ct1], y = decon_df[, ct2])) +
    geom_point() +
    ggpubr::stat_cor(method = "pearson",label.y = max(decon_df[, ct2]) + 0.05) +
    labs(x = stringr::str_wrap(sprintf("%s proportion", ct1), width = 30),
         y = stringr::str_wrap(sprintf("%s proportion", ct2), width = 30)) +
    theme_classic()
  }) %>%
  cowplot::plot_grid(
    plotlist = .,
    nrow = 4,
    ncol = 4,
    align = "hv",
    axis = "trbl")

# cowplot::save_plot(filename = sprintf("%s/%s/scater_cor_plot_breast_%s.pdf",
#                        an_breast_10x, plt_dir, slice),
#                    plot = corr_plts,
#                    base_height = 12,
#                    base_width = 16)

"{an_breast_10x}/{plt_dir}/scater_cor_plot_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = corr_plts,
    base_height = 12,
    base_width = 16)
```

Lastly we are going to plot pairs of interest for the main figure
```{r eval = FALSE}
if (clust_vr == "lv2_annot") {
  pairs_int <- c("Proliferation-CD8.IFN.activated",
                 "Proliferation-CD4.activated",
                 "CD8.exhausted-T.helper.Th17",
                 "CD4.activated-TAMs.C1QC",
                 "NK-TAMs.C1QC",
                 "CD8.exhausted-TAMs.C1QC")
} else if (clust_vr == "lv1_annot") {
  pairs_int <- c("TAMs C1QC-Macrophages SPP1",
                 "Proliferation-Macrophages SPP1",
                 "Proliferation-CD8 terminally exhausted",
                 "TAMs C1QC-CD8 terminally exhausted",
                 "TAMs C1QC-NK",
                 "Proliferation-NK")
}
```

Iterate over the pairs
```{r eval = FALSE}
decon_df <- metadata %>%
  dplyr::select(all_of(ct))
  # Remove cell types not predicted to be on the tissue
decon_df <- decon_df[, colSums(decon_df) > 0]

scater_interest <- lapply(pairs_int, function(i) {
  # separate ct_12
  str_ls <- stringr::str_split(string = i, pattern = "-",simplify = TRUE)
  ct1 <-str_ls[[1]]
  ct2 <-str_ls[[2]]
  
  ggplot(decon_df,
         aes(x = decon_df[, ct1], y = decon_df[, ct2])) +
    geom_point() +
    ggpubr::stat_cor(method = "pearson",
                     label.y = max(decon_df[, ct2]) + 0.05,
                     size = 5) +
    labs(x = stringr::str_wrap(sprintf("%s proportion", ct1), width = 30),
         y = stringr::str_wrap(sprintf("%s proportion", ct2), width = 30)) +
    theme_classic() +
    theme(
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 20))
  }) %>%
  cowplot::plot_grid(
    plotlist = .,
    nrow = 3,
    ncol = 2,
    align = "hv",
    axis = "trbl")

scater_interest

"{an_breast_10x}/{plt_dir}/scater_cor_plot_{sample_id}_{clust_vr}_interest.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = scater_interest,
    base_height = 16,
    base_width = 12)
```

## Session Info
```{r}
sessionInfo()
```

