---
author: "Marc Elosua-Bayes"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    df_print: paged
editor_options: 
  chunk_output_type: console
params: 
    sample_id: "Default!"
    clust_vr: "lv1_annot"
title: "`r sprintf('RCTD-10x_breast_immune_reference %s', {params$sample_id})`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "100%", fig.align='center', 
                      message = FALSE, warning = FALSE)
options(width = 1200)
```

## Introduction
In this R markdown document we will compare the deconvolution obtained from SPOTlight and RCTD.

RCTD original paper can be found [here](https://doi.org/10.1038/s41587-021-00830-w) and the GitHub repo [here](https://github.com/dmcable/RCTD).


```{r}
library(Seurat)
library(tidyverse)
library(Matrix)
# devtools::install_github("dmcable/RCTD", build_vignettes = TRUE)
library(RCTD)
source(here::here("utils/bin.r"))
```

## Paths
```{r}
source(here::here("misc/paths.R"))

"{an_breast_10x}/{robj_dir}" %>%
  glue::glue() %>%
  here::here() %>%
  dir.create(
    path = ,
    showWarnings = FALSE,
    recursive = TRUE)

"{an_breast_10x}/{plt_dir}" %>%
  glue::glue() %>%
  here::here() %>%
  dir.create(
    path = ,
    showWarnings = FALSE,
    recursive = TRUE)
```

## Parameters
```{r}
set.seed(1243)

sample_id <- params$sample_id
# sample_id <- "breast_2"
# clust_vr <- params$clust_vr
clust_vr <- "lv1_annot"
# clust_vr <- "lv2_annot"

trn <- "melanoma"
cl_n <- 100
hvg <- 3000
ntop <- NULL
transf <- "uv"
method <- "nsNMF"
min_cont <- 0

if (is.null(ntop)) {
  spotlight_id <- glue::glue("trn-{trn}_cln-{cl_n}_hvg-{hvg}_ntop-NULL_transf-{transf}_method-{method}_mincont-{min_cont}")
} else {
  spotlight_id <- glue::glue("trn-{trn}_cln-{cl_n}_hvg-{hvg}_ntop-{ntop}_transf-{transf}_method-{method}_mincont-{min_cont}")
}
```

Create a name/color dataframe
```{r}
# source(here::here("misc/col_df_scrpt.R"))
# source(here::here("misc/col_df_scrpt2.R"))
col_df <- readRDS(here::here("misc/col_df.rds"))
```

## Load data
Load spatial object
```{r}
### Spatial breast cancer
se_obj <- "{an_breast_10x}/{robj_dir}/qc_se_{sample_id}.rds" %>%
  glue::glue() %>%
  here::here() %>%
  readRDS(file = .)
```

SPOTlight deconvolution
```{r}
decon_mtrx_ls <- "{an_breast_10x}/{robj_dir}/decon_mtrx_breast_cancer_10x_atlas_{sample_id}_{spotlight_id}_{clust_vr}.rds" %>%
  glue::glue() %>%
  here::here() %>%
  readRDS(file = .)
```

RCTD deconvolution
```{r}
myRCTD <- "{an_breast_10x}/{robj_dir}/RCTDobj_{sample_id}_{clust_vr}.rds" %>%
  glue::glue() %>%
  here::here() %>%
  readRDS(file = .)
```

## Analysis

### Extract deconvolutions

SPOTlight extraction and renaming
```{r}
decon_mtrx <- decon_mtrx_ls[[2]]
decon_mtrx <- decon_mtrx[, colnames(decon_mtrx) != "res_ss"]

# Set as 0 cell types predicted to be under 5 % of the spot
# decon_mtrx[decon_mtrx < 0.05] <- 0

# Change names to original ones and reorder according to Paula
new_colnames <- data.frame(ct_name = colnames(decon_mtrx), stringsAsFactors = FALSE) %>%
  dplyr::left_join(col_df, by = "ct_name") %>%
  dplyr::pull(plt_name)

colnames(decon_mtrx) <- new_colnames


colnames(decon_mtrx) <- glue::glue("SPOTlight-{colnames(decon_mtrx)}")
rownames(decon_mtrx) <- colnames(se_obj)
```

RCTD extraction
```{r}
RCTD_mtrx <- as.matrix(myRCTD@results[[1]])
colnames(RCTD_mtrx) <- glue::glue("RCTD-{colnames(RCTD_mtrx)}")
# RCTD_mtrx[RCTD_mtrx < 0.05] <- 0

# Normalize RCTD matrix to 1
RCTD_mtrx <- RCTD_mtrx / rowSums(RCTD_mtrx)
```

Add deconvolution matrices to Seurat object
```{r}
rownames(RCTD_mtrx) <- stringr::str_replace(
  string = rownames(RCTD_mtrx),
  pattern = "\\.",
  replacement = "-")

barcodes <- purrr::reduce(list(rownames(se_obj@meta.data),
                   rownames(RCTD_mtrx),
                   rownames(decon_mtrx)),
              dplyr::intersect)

RCTD_mtrx <- RCTD_mtrx[barcodes, ]
decon_mtrx <- decon_mtrx[barcodes, ]

se_obj@meta.data <- cbind(se_obj@meta.data[barcodes, ],
                          RCTD_mtrx[barcodes, ],
                          decon_mtrx[barcodes, ])
```

### Deconvolution comparison
Here we are going to compare RCTD and SPOTlight deconvolutions by correlating the cell types
```{r fig.width=20, fig.height=20}
cor_plots <- lapply(colnames(decon_mtrx), function(i) {
  print(i)
  i_spot <- i
  i_sub <- stringr::str_split(string = i, pattern = "-", simplify = TRUE, n = 2)
  i_rctd <- glue::glue("RCTD-{i_sub[2]}")
  
  dat <- data.frame(
    SPOTlight = decon_mtrx[, i_spot],
    RCTD = RCTD_mtrx[, i_rctd],
    check.names = FALSE)
  
  print(cor.test(decon_mtrx[, i_spot],
           RCTD_mtrx[, i_rctd]))
  
  ggpubr::ggscatter(dat, x = "SPOTlight", y = "RCTD",
     color = "black",
     add = "reg.line",  # Add regressin line
     add.params = list(color = "blue", fill = "lightgray"), # Customize reg. line
     cor.coef = TRUE, # Add correlation coefficient. see ?stat_cor
     cor.coeff.args = list(method = "pearson", label.sep = "\n"),
     title = i_sub[2])
  })


plt_grid <- cowplot::plot_grid(plotlist = cor_plots,align = "hv", axis = "trbl")

"{an_breast_10x}/{plt_dir}/cor_grid_RCTD-SPOTlight_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = plt_grid,
    base_height = 20,
    base_width = 20)
```

### Visualize cell types
Next we want to visualize the cell types side by side
```{r}
tissue_plots <- lapply(colnames(decon_mtrx), function(i) {
  print(i)
  i_spot <- i
  i_sub <- stringr::str_split(string = i, pattern = "-", simplify = TRUE, n = 2)
  i_rctd <- glue::glue("RCTD-{i_sub[2]}")
  
  Seurat::SpatialPlot(
    object = se_obj,
    features = c(i_spot, i_rctd),
    alpha = c(0, 1),
    image.alpha = 1)
})


tissue_grid <- cowplot::plot_grid(plotlist = tissue_plots,
                                  align = "hv",
                                  axis = "trbl")

"{an_breast_10x}/{plt_dir}/tissue_grid_RCTD-SPOTlight_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = tissue_grid,
    base_height = 25,
    base_width = 35)
```

## Session Info
```{r}
sessionInfo()
```
