---
author: "Marc Elosua-Bayes"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  BiocStyle::html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
    df_print: paged
editor_options: 
  chunk_output_type: console
params: 
    sample_id: "Default!"
    clust_vr: "Default!"
title: "`r sprintf('4-Australia oropharyngeal cancer stratification %s', {params$sample_id})`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, out.width = "100%", fig.align='center', 
                      message = FALSE, warning = FALSE)
options(width = 1200)
```

## Introduction
In this Rmarkdown document we are going to stratify the tissue and analyze the differences in proportions and prevalence between the stratified regions.
Regions have been obtained by clustering in Seurat and following a pathologist's annotation.

## Libraries
```{r}
library(Seurat)
library(dplyr)
library(ggplot2)
library(purrr)
library(SPOTlight)
source(here::here("misc/paths.R"))
source(here::here("utils/bin.r"))
```

## Parameters
```{r}
set.seed(1243)

sample_id <- params$sample_id
# sample_id <- "161429"
# sample_id <- "161430"
clust_vr <- params$clust_vr
# clust_vr <- "lv2_annot"
# clust_vr <- "lv1_annot"

trn <- "melanoma"
cl_n <- 100
hvg <- 3000
ntop <- NULL
transf <- "uv"
method <- "nsNMF"
min_cont <- 0

if (is.null(ntop)) {
  spotlight_id <- glue::glue("trn-{trn}_cln-{cl_n}_hvg-{hvg}_ntop-NULL_transf-{transf}_method-{method}_mincont-{min_cont}")
} else {
  spotlight_id <- glue::glue("trn-{trn}_cln-{cl_n}_hvg-{hvg}_ntop-{ntop}_transf-{transf}_method-{method}_mincont-{min_cont}")
}
```

```{r}
if (clust_vr == "lv2_annot") {
  ct_interest <- c("Plasma.B cells", "T.regs", "T.helper.Th17",
                 "Proliferation", "CD8.exhausted",
                 "CD8.cytotoxic", "NK", "Macrophages.SPP1", "TAMs.C1QC")
} else if (clust_vr == "lv1_annot") {
  ct_interest_dict <- list()
  
  ct_interest_dict[["161429"]] <- list(
    c("B cells", "Plasma B cells", "T cells regulatory",
      "CD8 terminally exhausted", "Macrophages SPP1", "TAMs C1QC",
      "cDC", "Proliferation"),
    c(4, 2))
  
  ct_interest_dict[["161430"]] <- list(
    c("Plasma B cells", "T cells regulatory", "CD8 pre-exhausted",
      "Macrophages SPP1", "TAMs C1QC", "CD8 cytotoxic",
      "Proliferation", "CD4 naive-memory"),
    c(3, 2))
}
```

## Load data
We are going to start by loading the data from the previous scripts *1-australis_oroph_processing.Rmd* and *3-australia_oroph_deconv.Rmd*.
```{r}
se_obj <- "{an_oro}/{robj_dir}/processed_sp_oropharyngeal_{sample_id}.RDS" %>%
  glue::glue() %>%
  here::here() %>%
  readRDS(file = .)

decon_mtrx_ls <- "{an_oro}/{robj_dir}/decon_mtrx_atlas_{sample_id}_{spotlight_id}_{clust_vr}.rds" %>%
  glue::glue() %>%
  here::here() %>%
  readRDS(file = .)
```

Create a name/color dataframe
```{r}
# source(here::here("misc/col_df_scrpt.R"))
# source(here::here("misc/col_df_scrpt2.R"))
col_df <- readRDS(here::here("misc/col_df.rds"))
```

Change names to original ones and reorder according to Paula
```{r}
decon_mtrx <- decon_mtrx_ls[[2]]
decon_mtrx <- decon_mtrx[, colnames(decon_mtrx) != "res_ss"]

# Set as 0 cell types predicted to be under 3 % of the spot
decon_mtrx[decon_mtrx < 0.03] <- 0

new_colnames <- data.frame(ct_name = colnames(decon_mtrx), stringsAsFactors = FALSE) %>%
  dplyr::left_join(col_df, by = "ct_name") %>%
  dplyr::pull(plt_name)

colnames(decon_mtrx) <- new_colnames
```

Set paula order sub for subsequent use
```{r}
ct <- colnames(decon_mtrx)[!colnames(decon_mtrx) %in% "res_ss"]
```

## Stratify tissue
Add deconvolution matrix to Seurat object metadata
```{r}
se_obj@meta.data <- cbind(se_obj@meta.data, round(decon_mtrx, 3))
```

Stratify the tissue:
```{r}
if (sample_id == "161429") {
  se_obj@meta.data[, "Stratification"] <- se_obj@meta.data[, "SCT_snn_res.0.1"]
} else if (sample_id == "161430") {
  se_obj@meta.data[, "Stratification"] <- se_obj@meta.data[, "SCT_snn_res.0.09"]
}
```

Format the data into long format
```{r}
metadata_long <- se_obj@meta.data %>% 
  tidyr::pivot_longer(cols = all_of(ct),
                      names_to = "immune_key",
                      values_to = "immune_val") %>%
  dplyr::left_join(col_df,
                   by = c("immune_key" = "ct_name")) %>%
  dplyr::mutate(immune_val = dplyr::if_else(immune_val > 0.001, immune_val, 0))

```

### Visualization
#### BoxPlots
Box plot of cell type proportion between stratified regions showing the unadjusted ANOVA Pvalue
```{r}
# https://stackoverflow.com/questions/28436855/change-the-number-of-breaks-using-facet-grid-in-ggplot2
# defining the breaks function, 
# s is the scaling factor (cf. multiplicative expand)
equal_breaks <- function(n = 3, s = 0.05, ...){
  function(x){
    # rescaling
    d <- s * diff(range(x)) / (1 + 2 * s)
    round(seq(min(x) + d, max(x) - d, length = n), 2)
    }
}

# find cell types that are expressed in at least 1 spot
keep_ct <- metadata_long %>%
  dplyr::group_by(immune_key) %>%
  dplyr::summarise(prop_sum = sum(immune_val)) %>% 
  dplyr::filter(prop_sum > 0) %>%
  dplyr::pull(immune_key)

# Plot boxplot
bplt_tmp <- metadata_long %>%
  dplyr::filter(immune_key %in% keep_ct) %>%
  dplyr::mutate(
    immune_key = stringr::str_wrap(string = immune_key,
                                   width = 20)) %>%
  # dplyr::filter(! plt_name %in% c("CD8 EM-like", "CD4 naive-like")) %>%
  ggpubr::ggboxplot(data = .,
                    x = "Stratification",
                    y = "immune_val",
                    facet.by = "immune_key",
                    color = "Stratification",
                    fill = "Stratification",
                    add = "jitter",
                    scales = "free",
                    repel = TRUE,
                    outlier.shape = NA,
                    alpha = 0.6,
                    palette = c("#E41A1C", "#4DAF4A", "#377EB8", "#984EA3") # Set1 adaptation
                    ) +
  # Set 3 breaks
  ggplot2::scale_y_continuous(
    # Add padding on top
    # expand = ggplot2::expansion(mult = c(0, 0.1)),
    breaks = equal_breaks(n = 3, s = 0.05),
    expand = c(0.05, 0),
    labels = function(x) sapply(x, FUN = function(i) format(x = i, nsmall = 0))) +
  ggplot2::theme(
    strip.text = ggplot2::element_text(size = 18, face = "bold"),
    axis.text.y = ggplot2::element_text(size = 16),
    axis.text.x = ggplot2::element_text(size = 12),
    legend.text = ggplot2::element_text(size = 18),
    strip.background = ggplot2::element_blank()) +
  ggplot2::labs(x = "Stratification",
       y = "Proportion",
       color = "Regions",
       fill = "Regions")
  
## Add P values
bplt_tmp <- bplt_tmp +
  ggpubr::stat_compare_means(method = "anova", size = 6)

"{an_oro}/{plt_dir}/strat_bplot_oro_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = bplt_tmp,
    base_height = 25,
    base_width = 25)
```

Box plot of cell type proportion of interest between stratified regions showing the unadjusted ANOVA Pvalue
```{r fig.width=25, fig.height=25}
if (clust_vr == "lv1_annot") {
  # Keep cell types of interest
  keep_ct <- ct_interest_dict[[sample_id]][[1]]
} else if (clust_vr == "lv2_annot") {
  keep_ct <- ct
}

# Plot boxplot
bplt_tmp2 <- metadata_long %>%
  dplyr::filter(immune_key %in% keep_ct) %>%
  dplyr::mutate(
    immune_key = stringr::str_wrap(string = immune_key,
                                   width = 25)) %>%
  # dplyr::filter(! plt_name %in% c("CD8 EM-like", "CD4 naive-like")) %>%
  ggpubr::ggboxplot(data = .,
                    x = "Stratification",
                    y = "immune_val",
                    facet.by = "immune_key",
                    color = "Stratification",
                    fill = "Stratification",
                    add = "jitter",
                    scales = "free",
                    repel = TRUE,
                    outlier.shape = NA,
                    alpha = 0.6,
                    palette = c("#E41A1C", "#4DAF4A", "#377EB8", "#984EA3"),  # Set1 adaptation
                    ncol = ct_interest_dict[[sample_id]][[2]][[2]]
                    ) +
  # Set 3 breaks
  ggplot2::scale_y_continuous(
    # Add padding on top
    # expand = ggplot2::expansion(mult = c(0, 0.1)),
    breaks = equal_breaks(n = 3, s = 0.05),
    expand = c(0.05, 0),
    labels = function(x) sapply(x, FUN = function(i) format(x = i, nsmall = 0))) +
  ggplot2::theme(
    strip.text = ggplot2::element_text(size = 30, face = "bold"),
    axis.text.y = ggplot2::element_text(size = 20),
    axis.text.x = ggplot2::element_text(size = 20),
    axis.title = ggplot2::element_text(size = 25),
    panel.grid.major = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank(),
    strip.background = ggplot2::element_blank(),
    panel.border = ggplot2::element_rect(colour = "black"),
    legend.text = ggplot2::element_text(size = 22),
    legend.title = ggplot2::element_blank()) +
  ggplot2::labs(x = "Stratification",
       y = "Proportion",
       color = "Regions",
       fill = "Regions")

  # guides(color = guide_legend(override.aes = list(size = 3)))
  
(bplt_pval <- bplt_tmp2 +
  ggpubr::stat_compare_means(method = "anova", size = 8) +
  ggplot2::scale_y_continuous(
    expand = expansion(mult = c(0, 0.1)),
    labels = function(x) sprintf("%.2f", x)) +
  ggplot2::theme(
    axis.text = ggplot2::element_text(size = 15),
    strip.text = ggplot2::element_text(size = 30),
    axis.title = ggplot2::element_text(size = 25)
  ))

"{an_oro}/{plt_dir}/strat_bplot_oro_{sample_id}_{clust_vr}_interest.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = bplt_tmp2,
    base_height = 15,
    base_width = 15)

```

#### Heatmap
Proportion heatmap, Here we look at the proportion of spots within each stratified regions contains a cell type regardless of its proportion.
```{r}
tmp_df <- se_obj@meta.data %>%
  # dplyr::select(-c("res_ss")) %>%
  dplyr::mutate(total = 1) %>%
  dplyr::select(all_of(c(ct, "total", "Stratification"))) %>%
  tidyr::pivot_longer(cols = all_of(ct)) %>%
  dplyr::mutate(value = if_else(value < 0.001, 0, 1)) %>%
  dplyr::group_by(name, Stratification) %>%
  dplyr::summarise(freq = sum(value) / sum(total))

# Plot heatmap
hm_tmp <- tmp_df %>%
  ggplot(aes(x = Stratification, 
             y = name, 
             fill= freq)) + 
  geom_tile(color = "lightgrey") +
  geom_text(aes(label = round(freq, 2)), 
            show.legend = FALSE) +
  labs(title = "Oropharyngeal cancer cell-type enrichment by region",
       y = "Cell types", 
       x = "",
       fill = "Proportion") +
  theme_classic() +
  scale_y_discrete(limits = rev(ct),
                   labels = stringr::str_wrap(string = rev(ct),
                                              width = 21)) +
  scale_fill_gradient(low = "#FFF5F0",
                      high = "#99000D",
                      guide = "legend",
                      limits = c(0, 1),
                      breaks = seq(0, 1, 0.1)) +
  scale_alpha_continuous(guide = "legend",
                         limits = c(0, 1), 
                         breaks = seq(0, 1, 0.1)) +
  theme(axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 17),
        plot.title = element_text(hjust = 0.5, face = "bold", size = 18),
        axis.title = element_text(size = 15),
        axis.line = element_blank())

"{an_oro}/{plt_dir}/strat_heatmap_oro_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = hm_tmp,
    base_height = 15,
    base_width = 9)

# Plot heatmap without text
hm_tmp2 <- tmp_df %>%
  ggplot(aes(x = Stratification, 
             y = name, 
             fill= freq)) + 
  geom_tile(color = "lightgrey") +
  labs(title = "Oropharyngeal cancer cell-type enrichment by region",
       y = "Cell types", 
       x = "",
       fill = "Proportion") +
  theme_classic() +
  scale_y_discrete(limits = rev(ct)) +
  scale_fill_gradient(low = "#FFF5F0",
                      high = "#99000D",
                      guide = "legend",
                      limits = c(0, 1),
                      breaks = seq(0, 1, 0.1)) +
  scale_alpha_continuous(guide = "legend",
                         limits = c(0, 1), 
                         breaks = seq(0, 1, 0.1)) +
  theme(axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5),
        axis.text.y = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 17),
        plot.title = element_text(hjust = 0.5, face = "bold", size = 18),
        axis.title = element_text(size = 15),
        axis.line = element_blank())

"{an_oro}/{plt_dir}/strat_heatmap_oro_{sample_id}_{clust_vr}_labelless.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = hm_tmp2,
    base_height = 15,
    base_width = 9)
```

## Cell-Cell correlation plot
By looking at correlations we want to assess if there are cell types which are correlating in space. So when one is present is another one also present?

We will be using `ggcorrplot` to show these correlation plots a bit nicer:
http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2
<!-- http://www.sthda.com/english/wiki/visualize-correlation-matrix-using-correlogram -->

Get correlation matrix between all cell types
```{r}
decon_df <- se_obj@meta.data %>%
  dplyr::select(all_of(ct))

# Remove cell types not predicted to be on the tissue
decon_df <- decon_df[, colSums(decon_df) > 0]
decon_cor <- cor(decon_df)

# Compute correlation P-value
p.mat <- corrplot::cor.mtest(mat = decon_df, conf.level = 0.95)
colnames(decon_cor) <- stringr::str_wrap(
  string = colnames(decon_cor),
  width = 30)
rownames(decon_cor) <- stringr::str_wrap(
  string = rownames(decon_cor),
  width = 30)


cor_plt <- ggcorrplot::ggcorrplot(corr = decon_cor,
           p.mat = p.mat[[1]],
           hc.order = TRUE,
           type = "full",
           insig = "blank",
           lab = TRUE,
           outline.col = "lightgrey",
           method = "square",
           # colors = c("#4477AA", "white", "#BB4444"))
           colors = c("#6D9EC1", "white", "#E46726"),
           title = "Oropharyngeal carcinoma cell-cell proportion correlation",
           legend.title = "Correlation\n(Pearson)") +
   theme(
    plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
    legend.text = element_text(size = 12),
    legend.title = element_text(size = 15),
    axis.text.x = element_text(angle = 90),
    axis.text = element_text(size = 18, vjust = 0.5))
cor_plt
# cowplot::save_plot(plot = cor_plt,
#                  filename = sprintf("%s/%s/correlation_plot_breast_%s.pdf",
#                      an_oro, plt_dir, i),
#                  base_width = 16,
#                  base_height = 12)

"{an_oro}/{plt_dir}/correlation_plot_{sample_id}_{clust_vr}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = cor_plt,
    base_height = 16,
    base_width = 12)

# Now without labels
cor_plt2 <- ggcorrplot::ggcorrplot(corr = decon_cor,
           p.mat = p.mat[[1]],
           hc.order = TRUE,
           type = "full",
           insig = "blank",
           lab = FALSE,
           outline.col = "lightgrey",
           method = "square",
           # colors = c("#4477AA", "white", "#BB4444"))
           colors = c("#6D9EC1", "white", "#E46726"),
           title = glue::glue("Oropharyngeal carcinoma cell-cell proportion correlation \n Sample-{sample_id}"),
           legend.title = "Correlation\n(Pearson)") +
  theme(
    plot.title = element_text(size = 25, hjust = 0.5, face = "bold"),
    legend.text = element_text(size = 18),
    legend.title = element_text(size = 22),
    axis.text.x = element_text(angle = 90, size = 18, vjust = 0.5),
    axis.text.y = element_text(vjust = 0.5, size = 18))

cor_plt2

"{an_oro}/{plt_dir}/correlation_plot_{sample_id}_{clust_vr}_labelless.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = cor_plt2,
    base_height = 16,
    base_width = 12)
```

Lastly we are going to plot pairs of interest for the main figure
```{r eval = FALSE}
if (clust_vr == "lv2_annot") {
  pairs_int <- c("Proliferation-CD8.IFN.activated",
                 "Proliferation-CD4.activated",
                 "CD8.exhausted-T.helper.Th17",
                 "CD4.activated-TAMs.C1QC",
                 "NK-TAMs.C1QC",
                 "CD8.exhausted-TAMs.C1QC")
} else if (clust_vr == "lv1_annot") {
  if (sample_id == "161429") {
    pairs_int <- c("B cells/Proliferation",
                   "B cells/cDC",
                   "T cells regulatory/CD8 cytotoxic",
                   "T cells regulatory/CD8 terminally exhausted",
                   "TAMs C1QC/Macrophages SPP1",
                   "Proliferation/Macrophages SPP1"
                   )
  } else if (sample_id == "161430") {
    pairs_int <- c("TAMs C1QC/Proliferation",
                   "TAMs C1QC/CD8 terminally exhausted",
                   "TAMs C1QC/Macrophages SPP1",
                   "Proliferation/Macrophages SPP1",
                   "T cells regulatory/CD8 terminally exhausted",
                   "Proliferation/CD4 recently activated",
                   "Proliferation/CD8 terminally exhausted"
                   )
  }
}
```

Iterate over the pairs
```{r eval = FALSE}
# Remove cell types not predicted to be on the tissue
decon_df <- decon_df[, colSums(decon_df) > 0]

scater_interest <- lapply(pairs_int, function(i) {
  print(i)
  # separate ct_12
  str_ls <- stringr::str_split(string = i, pattern = "/",simplify = TRUE)
  ct1 <-str_ls[[1]]
  ct2 <-str_ls[[2]]
  
  ggplot(decon_df,
         aes(x = decon_df[, ct1], y = decon_df[, ct2])) +
    geom_point() +
    ggpubr::stat_cor(method = "pearson",
                     label.y = max(decon_df[, ct2]) + 0.05,
                     size = 5) +
    labs(x = stringr::str_wrap(glue::glue("{ct1} proportion"), width = 30),
         y = stringr::str_wrap(glue::glue("{ct2} proportion"), width = 30)) +
    theme_classic() +
    theme(
      axis.text = element_text(size = 16),
      axis.title = element_text(size = 20))
  }) %>%
  cowplot::plot_grid(plotlist = ., nrow = 3,ncol = 2)

scater_interest

"{an_oro}/{plt_dir}/scater_cor_plot_{sample_id}_{clust_vr}_interest.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = scater_interest,
    base_height = 16,
    base_width = 12)
```

#### Markers
TGFB1 is a known fibrotic marker.
```{r}
sp_cl <- Seurat::SpatialDimPlot(object = se_obj,
                                group.by = "SCT_snn_res.0.1")

sp_tmp <- Seurat::SpatialFeaturePlot(object = se_obj,
                           features = "TGFB1",
                           alpha = c(0, 1))

vln_tmp <- Seurat::VlnPlot(object = se_obj,
                           features = "TGFB1",
                           group.by = "SCT_snn_res.0.1",
                           assay = "SCT",
                           slot = "data")

tmp <- sp_cl + sp_tmp + vln_tmp
tmp

"{an_oro}/{plt_dir}/fibrotic_marker_{sample_id}.pdf" %>%
  glue::glue() %>%
  here::here() %>%
  cowplot::save_plot(
    filename = .,
    plot = tmp,
    base_height = 6,
    base_width = 15)
```

```{r}
chart.Correlation(decon_df, histogram=TRUE, pch=19)
```

## Session Info
```{r}
sessionInfo()
```

