---
title: "4-Australia oropharyngeal cancer stratification"
author: "Marc Elosua Bayés"
date: "9/8/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
In this Rmarkdown document we are going to stratify the tissue and analyze the differences in proportions and prevalence between the stratified regions.
Regions have been obtained by clustering in Seurat and following a pathologist's annotation.

## Libraries
```{r}
library(Seurat)
library(dplyr)
library(ggplot2)
library(matchSCore2)
library(purrr)
library(SPOTlight)
source("misc/paths.R")
source("utils/bin.r")
source("utils/spatial_plot_spaniel.R")
```

## Parameters
```{r}
trn <- "melanoma"
cl_n <- 100
hvg <- 3000
ntop <- NULL
transf <- "uv"
method <- "nsNMF"
min_cont <- 0
clust_vr <- "new_cell_types"

if (is.null(ntop)) {
  spotlight_id <- sprintf("trn-%s_cln-%s_hvg-%s_ntop-NULL_transf-%s_method-%s_mincont-%s",
                          trn, cl_n, hvg, transf, method, min_cont)
} else {
  spotlight_id <- sprintf("trn-%s_cln-%s_hvg-%s_ntop-%s_transf-%s_method-%s_mincont-%s",
                          trn, cl_n, hvg, ntop, transf, method, min_cont)
}

ct_interest_dict <- list()
ct_interest_dict[["161429"]] <- list(c("B cells", "Naive-memory CD4 T cells", "Cytotoxic CD8 T cells", "Terminally exhausted CD8 T cells", "M2 TAMs", "Regulatory T cells", "SPP1 TAMs", "Proliferative T cells"), c(4, 2))
ct_interest_dict[["161430"]] <- list(c("M2 TAMs", "SPP1 TAMs", "Regulatory T cells", "Proliferative T cells", "Terminally exhausted CD8 T cells", "Pre-exhausted CD8 T cells"), c(3, 2))
ct_interest_dict[["161431"]] <- list(c("B cells", "Pre-exhausted CD8 T cells", "M2 TAMs", "Effector memory CD8 T cells", "Terminally exhausted CD8 T cells", "NK"), c(3, 2))
ct_interest_dict[["161432"]] <- list(c("B cells", "Recently activated CD4 T cells", "Cytotoxic CD8 T cells", "Naive T cells", "Proliferative monocytes and macrophages", "SPP1 TAMs"), c(3, 2))
```

Source name/color dataframe
```{r}
source("misc/col_df_scrpt.R")
```

## Load data
We are going to start by loading the data from the previous scripts *1-australis_oroph_processing.Rmd* and *3-australia_oroph_deconv.Rmd*.
```{r}
st_ls <- readRDS(file = sprintf("%s/%s/processed_st_ls_oropharyngeal.RDS",
                       an_oro, robj_dir))

decon_paths <- list.files(path = sprintf("%s/%s",
                           an_oro, robj_dir),
               pattern = "spotlight_deconv_ls_.*.RDS",
               full.names = TRUE)

decon_nms <- stringr::str_split(string = decon_paths,
                   pattern = "/|_",
                   simplify = TRUE)[, 11]


decon_ls <- lapply(decon_paths, function(pth) readRDS(file = pth))

names(decon_ls) <- decon_nms
```

Change names to original ones and reorder according to Paula
```{r}
for (nm in names(decon_ls)) {
  decon_mtrx <- decon_ls[[nm]][[2]]
  decon_mtrx <- decon_mtrx[, colnames(decon_mtrx) != "res_ss"]
  
  # Set as 0 cell types predicted to be under 0.1 % of the spot
  decon_mtrx[decon_mtrx < 0.001] <- 0
  
  new_colnames <- data.frame(ct_name = colnames(decon_mtrx), stringsAsFactors = FALSE) %>%
    dplyr::left_join(col_df, by = "ct_name") %>%
    dplyr::pull(plt_name)
  
  colnames(decon_mtrx) <- new_colnames
  
  paula_order[! paula_order %in% colnames(decon_mtrx)]
  decon_ls[[nm]][[2]] <- decon_mtrx[, paula_order]
}
```

## Stratify tissue
As we await for the pathologists annotation we are going to use the Seurat clusters as the basis of stratification.
We join the deconvolution matrix with the Seurat object metadata:
```{r}
decon_mtrx_ls <- sapply(decon_ls, function(i) return(i[[2]]), USE.NAMES = TRUE)

for (nm in names(st_ls)) {
  st_ls[[nm]]@meta.data <- cbind(st_ls[[nm]]@meta.data, decon_mtrx_ls[[nm]])
}
```

Stratify the tissue:
```{r}
for (nm in names(st_ls)) {
  st_ls[[nm]]@meta.data[, "Stratification"] <- st_ls[[nm]]@meta.data[, "SCT_snn_res.0.1"]
}
```

Format the data into long format
```{r}
long_metadata_ls <- lapply(names(st_ls), function(nm) {
  print(nm)
  metadata_long <- st_ls[[nm]]@meta.data %>% 
    tidyr::pivot_longer(cols = all_of(paula_order),
                        names_to = "immune_key",
                        values_to = "immune_val") %>%
    dplyr::left_join(col_df,
                     by = c("immune_key" = "ct_name")) %>%
    dplyr::mutate(immune_val = dplyr::if_else(immune_val > 0.001, immune_val, 0))
  
  print(metadata_long %>% dplyr::count(immune_key))
  return(metadata_long)
})

names(long_metadata_ls) <- names(st_ls)
```

### Visualization
#### BoxPlots
Box plot of cell type proportion between stratified regions showing the unadjusted ANOVA Pvalue
```{r}
lapply(names(long_metadata_ls), function(nm) {
  
  # Extract long dataframe
  metadata_long <- long_metadata_ls[[nm]]
  
  # find cell types that are expressed in at least 1 spot
  keep_ct <- metadata_long %>%
    dplyr::group_by(immune_key) %>%
    dplyr::summarise(prop_sum = sum(immune_val)) %>% 
    dplyr::filter(prop_sum > 0) %>%
    dplyr::pull(immune_key)
  
  # Plot boxplot
  bplt_tmp <- metadata_long %>%
    dplyr::filter(immune_key %in% keep_ct) %>%
    dplyr::mutate(
      immune_key = stringr::str_wrap(string = immune_key,
                                     width = 20)) %>%
    # dplyr::filter(! plt_name %in% c("CD8 EM-like", "CD4 naive-like")) %>%
    ggpubr::ggboxplot(data = .,
                      x = "Stratification",
                      y = "immune_val",
                      facet.by = "immune_key",
                      color = "Stratification",
                      fill = "Stratification",
                      add = "jitter",
                      scales = "free",
                      repel = TRUE,
                      outlier.shape = NA,
                      alpha = 0.6,
                      palette = c("#E41A1C", "#4DAF4A", "#377EB8", "#984EA3") # Set1 adaptation
                      ) +
    theme(
      strip.text = element_text(size = 18, face = "bold"),
      axis.text.y = element_text(size = 16),
      axis.text.x = element_text(size = 12),
      legend.text = element_text(size = 18)) +
    labs(x = "Stratification",
         y = "Proportion",
         color = "Regions",
         fill = "Regions")
    
  bplt_tmp <- bplt_tmp +
    ggpubr::stat_compare_means(method = "anova", size = 6) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.1)))
  
  cowplot::save_plot(filename = sprintf("%s/%s/strat_bplot_oro_%s.pdf",
                                        an_oro, plt_dir, nm),
                     plot = bplt_tmp,
                     base_height = 20,
                     base_width = 20)
  
})
```

Box plot of cell type proportion of interest between stratified regions showing the unadjusted ANOVA Pvalue
```{r}
lapply(names(long_metadata_ls), function(nm) {
  
  # Extract long dataframe
  metadata_long <- long_metadata_ls[[nm]]
  
  # Keep cell types of interest
  keep_ct <- ct_interest_dict[[nm]][[1]]
  
  # Plot boxplot
  bplt_tmp <- metadata_long %>%
    dplyr::filter(immune_key %in% keep_ct) %>%
    dplyr::mutate(
      immune_key = stringr::str_wrap(string = immune_key,
                                     width = 25)) %>%
    # dplyr::filter(! plt_name %in% c("CD8 EM-like", "CD4 naive-like")) %>%
    ggpubr::ggboxplot(data = .,
                      x = "Stratification",
                      y = "immune_val",
                      facet.by = "immune_key",
                      color = "Stratification",
                      fill = "Stratification",
                      add = "jitter",
                      scales = "free",
                      repel = TRUE,
                      outlier.shape = NA,
                      alpha = 0.6,
                      palette = c("#E41A1C", "#4DAF4A", "#377EB8", "#984EA3"),  # Set1 adaptation
                      ncol = ct_interest_dict[[nm]][[2]][[2]]) +
    theme(
      strip.text = element_text(size = 25, face = "bold"),
      axis.text.y = element_text(size = 18),
      axis.text.x = element_text(size = 18),
      axis.title = element_text(size = 22),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      strip.background = element_blank(),
      panel.border = element_rect(colour = "black"),
      legend.text = element_text(size = 22),
      legend.title = element_blank()) +
    labs(x = "Stratification",
         y = "Proportion",
         color = "Regions",
         fill = "Regions")
    # guides(color = guide_legend(override.aes = list(size = 3)))
    
  bplt_tmp <- bplt_tmp +
    ggpubr::stat_compare_means(method = "anova", size = 8) +
    scale_y_continuous(expand = expansion(mult = c(0, 0.1)))
  
  cowplot::save_plot(filename = sprintf("%s/%s/strat_bplot_oro_%s_interest.svg",
                                        an_oro, plt_dir, nm),
                     plot = bplt_tmp,
                     base_height = 20,
                     base_width = 20)
  
})
```

#### Heatmap
Proportion heatmap, Here we look at the proportion of spots within each stratified regions contains a cell type regardless of its proportion.
```{r}
lapply(names(st_ls), function(nm) {
  
  tmp_df <- st_ls[[nm]]@meta.data %>%
    # dplyr::select(-c("res_ss")) %>%
    dplyr::mutate(total = 1) %>%
    dplyr::select(all_of(c(paula_order, "total", "Stratification"))) %>%
    tidyr::pivot_longer(cols = all_of(paula_order)) %>%
    dplyr::mutate(value = if_else(value < 0.001, 0, 1)) %>%
    dplyr::group_by(name, Stratification) %>%
    dplyr::summarise(freq = sum(value) / sum(total))

  # Plot heatmap
  hm_tmp <- tmp_df %>%
    ggplot(aes(x = Stratification, 
               y = name, 
               fill= freq)) + 
    geom_tile(color = "lightgrey") +
    geom_text(aes(label = round(freq, 2)), 
              show.legend = FALSE) +
    labs(title = "Oropharyngeal cancer cell-type enrichment by region",
         y = "Cell types", 
         x = "",
         fill = "Proportion") +
    theme_classic() +
    scale_y_discrete(limits = rev(paula_order),
                     labels = stringr::str_wrap(string = rev(paula_order),
                                                width = 21)) +
    scale_fill_gradient(low = "#FFF5F0",
                        high = "#99000D",
                        guide = "legend",
                        limits = c(0, 1),
                        breaks = seq(0, 1, 0.1)) +
    scale_alpha_continuous(guide = "legend",
                           limits = c(0, 1), 
                           breaks = seq(0, 1, 0.1)) +
    theme(axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5),
          axis.text.y = element_text(size = 15),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 17),
          plot.title = element_text(hjust = 0.5, face = "bold", size = 18),
          axis.title = element_text(size = 15),
          axis.line = element_blank())
  
  cowplot::save_plot(filename = sprintf("%s/%s/strat_heatmap_oro_%s.pdf",
                                        an_oro, plt_dir, nm),
                     plot = hm_tmp,
                     base_height = 15,
                     base_width = 9)
  
  # Plot heatmap without text
  hm_tmp <- tmp_df %>%
    ggplot(aes(x = Stratification, 
               y = name, 
               fill= freq)) + 
    geom_tile(color = "lightgrey") +
    labs(title = "Oropharyngeal cancer cell-type enrichment by region",
         y = "Cell types", 
         x = "",
         fill = "Proportion") +
    theme_classic() +
    scale_y_discrete(limits = rev(paula_order)) +
    scale_fill_gradient(low = "#FFF5F0",
                        high = "#99000D",
                        guide = "legend",
                        limits = c(0, 1),
                        breaks = seq(0, 1, 0.1)) +
    scale_alpha_continuous(guide = "legend",
                           limits = c(0, 1), 
                           breaks = seq(0, 1, 0.1)) +
    theme(axis.text.x = element_text(size = 12, angle = 90, vjust = 0.5),
          axis.text.y = element_text(size = 15),
          legend.text = element_text(size = 12),
          legend.title = element_text(size = 17),
          plot.title = element_text(hjust = 0.5, face = "bold", size = 18),
          axis.title = element_text(size = 15),
          axis.line = element_blank())
  
  cowplot::save_plot(filename = sprintf("%s/%s/strat_heatmap_oro_%s_labelless.svg",
                                        an_oro, plt_dir, nm),
                     plot = hm_tmp,
                     base_height = 15,
                     base_width = 9)
})

```

#### Markers
TGFB1 is a known fibrotic marker.
```{r}
lapply(names(st_ls), function(nm) {
  st_se <- st_ls[[nm]]
  
  sp_cl <- Seurat::SpatialDimPlot(object = st_se,
                                  group.by = "SCT_snn_res.0.1")
  
  sp_tmp <- Seurat::SpatialFeaturePlot(object = st_se,
                             features = "TGFB1",
                             alpha = c(0, 1))
  
  vln_tmp <- Seurat::VlnPlot(object = st_se,
                             features = "TGFB1",
                             group.by = "SCT_snn_res.0.1",
                             assay = "SCT",
                             slot = "data")
  
  tmp <- sp_cl + sp_tmp + vln_tmp
  cowplot::save_plot(filename = sprintf("%s/%s/fibrotic_marker_%s.pdf",
                                        an_oro, plt_dir, nm),
                     plot = tmp)
})
```

## Session Info
```{r}
sessionInfo()
```

