---
title: "5-Australia oropharyngeal cancer plots"
author: "Marc Elosua-Bayes"
date: "9/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this Rmarkdown document we are going to plot the plots not requiring stratification for this data.
We are going to use data generated in *1-australis_oroph_processing.Rmd* and *3-australia_oroph_deconv.Rmd*

## Libraries
```{r}
library(Seurat)
library(dplyr)
library(ggplot2)
library(matchSCore2)
library(purrr)
library(SPOTlight)
source("misc/paths.R")
source("utils/bin.r")
source("utils/spatial_plot_spaniel.R")
```

## Parameters
```{r}
trn <- "melanoma"
cl_n <- 100
hvg <- 3000
ntop <- NULL
transf <- "uv"
method <- "nsNMF"
min_cont <- 0
clust_vr <- "new_cell_types"

if (is.null(ntop)) {
  spotlight_id <- sprintf("trn-%s_cln-%s_hvg-%s_ntop-NULL_transf-%s_method-%s_mincont-%s",
                          trn, cl_n, hvg, transf, method, min_cont)
} else {
  spotlight_id <- sprintf("trn-%s_cln-%s_hvg-%s_ntop-%s_transf-%s_method-%s_mincont-%s",
                          trn, cl_n, hvg, ntop, transf, method, min_cont)
}

ct_interest_dict <- list()
ct_interest_dict[["161429"]] <- list(c("B cells", "Naive-memory CD4 T cells", "Cytotoxic CD8 T cells", "Terminally exhausted CD8 T cells", "M2 TAMs", "Regulatory T cells", "SPP1 TAMs", "Proliferative T cells"), c(4, 2))
ct_interest_dict[["161430"]] <- list(c("M2 TAMs", "SPP1 TAMs", "Regulatory T cells", "Proliferative T cells", "Terminally exhausted CD8 T cells", "Pre-exhausted CD8 T cells"), c(2, 3))
ct_interest_dict[["161431"]] <- list(c("B cells", "Pre-exhausted CD8 T cells", "M2 TAMs", "Effector memory CD8 T cells", "Terminally exhausted CD8 T cells", "NK"), c(3, 2))
ct_interest_dict[["161432"]] <- list(c("B cells", "Recently activated CD4 T cells", "Cytotoxic CD8 T cells", "Naive T cells", "Proliferative monocytes and macrophages", "SPP1 TAMs"), c(3, 2))

```

Source name/color dataframe
```{r}
source("misc/col_df_scrpt.R")
```

## Load data
We are going to start by loading the data from the previous scripts *1-australis_oroph_processing.Rmd* and *3-australia_oroph_deconv.Rmd*.
```{r}
st_ls <- readRDS(file = sprintf("%s/%s/processed_st_ls_oropharyngeal.RDS",
                       an_oro, robj_dir))

decon_paths <- list.files(path = sprintf("%s/%s",
                           an_oro, robj_dir),
               pattern = "spotlight_deconv_ls_.*.RDS",
               full.names = TRUE)

decon_nms <- stringr::str_split(string = decon_paths,
                   pattern = "/|_",
                   simplify = TRUE)[, 11]


decon_ls <- lapply(decon_paths, function(pth) readRDS(file = pth))

names(decon_ls) <- decon_nms
```

Change names to original ones and reorder according to Paula
```{r}
for (nm in names(decon_ls)) {
  decon_mtrx <- decon_ls[[nm]][[2]]
  decon_mtrx <- decon_mtrx[, colnames(decon_mtrx) != "res_ss"]
  
  # Set as 0 cell types predicted to be under 0.1 % of the spot
  decon_mtrx[decon_mtrx < 0.001] <- 0
  
  new_colnames <- data.frame(ct_name = colnames(decon_mtrx), stringsAsFactors = FALSE) %>%
    dplyr::left_join(col_df, by = "ct_name") %>%
    dplyr::pull(plt_name)
  
  colnames(decon_mtrx) <- new_colnames
  
  paula_order[! paula_order %in% colnames(decon_mtrx)]
  decon_ls[[nm]][[2]] <- decon_mtrx[, paula_order]

}
```

We join the deconvolution matrix with the Seurat object metadata:
```{r}
decon_mtrx_ls <- sapply(decon_ls, function(i) return(i[[2]]), USE.NAMES = TRUE)

for (nm in names(st_ls)) {
  st_ls[[nm]]@meta.data <- cbind(st_ls[[nm]]@meta.data, decon_mtrx_ls[[nm]])
}
```

## Topic profiles
```{r}
lapply(names(decon_ls), function(nm) {
  decon_nmf <- decon_ls[[nm]][[1]]
  
  h <- NMF::coef(decon_nmf[[1]])

  # Extract coefficient labels
  train_labs <- data.frame(ct_name = decon_nmf[[2]]) %>%
    dplyr::left_join(col_df, by = "ct_name") %>%
    pull(plt_name)
  
  rownames(h) <- paste("Topic", 1:nrow(h), sep = " ")
  profile_plt <- SPOTlight::dot_plot_profiles_fun(h = h,
                                   train_cell_clust = str_wrap(train_labs, width = 30),
                                   clust_vr = "specific_cell_type_mod")

  cowplot::save_plot(filename = sprintf("%s/%s/ct_profiles_%s.svg",
                                        an_oro, plt_dir, nm),
                     plot = profile_plt[[2]] +
                       labs(
                         title = sprintf("Topic profiles by cell type - %s",
                                         nm),
                         x = "",
                         y = "") +
                       scale_x_discrete(limits = unique(str_wrap(train_labs, width = 30))) +
                       theme(axis.text = element_text(size = 22),
                             axis.text.x = element_text(hjust = 1, vjust = 0.5),
                             legend.title = element_text(size = 20, face = "bold"),
                             legend.text = element_text(size = 18),
                             # plot.title = element_blank()
                             plot.title = element_text(size = 30)
                             ),
                     base_height = 15,
                     base_width = 15)

})
```

## Cell type location
Look at the location of each cell type in each slice separately
```{r}
library(RColorBrewer)

lapply(names(st_ls), function(nm) {
  # Extract Seurat object
  se_st <- st_ls[[nm]]
  
  # Iterate over cell types
  ct_plt_ls <- lapply(paula_order, function(ct) {
  tmp_plt <- Seurat::SpatialFeaturePlot(object = se_st,
                                        features = ct,
                                        alpha = c(0, 1)) +
    scale_fill_gradientn(
      colors = heat.colors(10, rev = TRUE)) +
    scale_alpha(range = c(0, 1)) +
    labs(title = stringr::str_wrap(string = ct,
                                   width = 25),
         fill = "") +
    theme(plot.title = element_text(hjust = 0.5,
                                    size = 20,
                                    face = "bold"))
  
  if (sum(se_st@meta.data[, ct]) == 0) {
    tmp_plt <- suppressMessages(tmp_plt + scale_alpha(range = c(0,0)))
  }
  
  return(tmp_plt)
  })

  plt_arr <- cowplot::plot_grid(plotlist = ct_plt_ls,
                     axis = "trbl",
                     align = "hv",
                     nrow = 5,
                     ncol = 5)
  
  cowplot::save_plot(filename = sprintf("%s/%s/aussie_oro_immune_reference_arrangement_%s.pdf",
                                        an_oro, plt_dir, nm),
                     plot = plt_arr,
                     base_height = 25,
                     base_width = 25)
  
})
```

Now only for cell types of interest
```{r}
lapply(names(st_ls), function(nm) {
  # Extract Seurat object
  se_st <- st_ls[[nm]]
  
  # Iterate over cell types
  ct_plt_ls <- lapply(ct_interest_dict[[nm]][[1]], function(ct) {
  tmp_plt <- Seurat::SpatialFeaturePlot(object = se_st,
                                        features = ct,
                                        alpha = c(0, 1)) +
    scale_fill_gradientn(
      colors = heat.colors(10, rev = TRUE)) +
    # scale_alpha(range = c(0, 1)) +
    labs(title = stringr::str_wrap(string = ct,
                                   width = 25),
         fill = "") +
    theme(plot.title = element_text(hjust = 0.5,
                                    size = 25,
                                    face = "bold"),
          legend.text = element_text(size = 15)) +
  guides(fill = guide_legend(override.aes = list(size = 8)))
  
  if (sum(se_st@meta.data[, ct]) == 0) {
    tmp_plt <- suppressMessages(tmp_plt + scale_alpha(range = c(0,0)))
  }
  
  return(tmp_plt)
  })

  plt_arr <- cowplot::plot_grid(plotlist = ct_plt_ls,
                     axis = "trbl",
                     align = "hv",
                     nrow = ct_interest_dict[[nm]][[2]][[1]],
                     ncol = ct_interest_dict[[nm]][[2]][[2]])
  
  cowplot::save_plot(filename = sprintf("%s/%s/aussie_oro_immune_reference_arrangement_%s_interest.svg",
                                        an_oro, plt_dir, nm),
                     plot = plt_arr,
                     base_height = 25,
                     base_width = 18)
  
})

```

## Spatial scatterpie
### All cell types
Then we will plot the scatterpie for both slices to get a gist of what is going on
```{r}
lapply(names(st_ls), function(nm) {
  # Extract Seurat object
  se_st <- st_ls[[nm]]
  
  sct_plt1 <- SPOTlight::scatterpie_plot(se_obj = se_st,
                                         cell_types_all = paula_order,
                                         pie_scale = 0.4) +
            scale_fill_manual(values = col_df[col_df$plt_name %in% paula_order, "ct_col"],
                              breaks = paula_order) +
            coord_fixed(ratio = 1) +
            guides(fill = guide_legend(ncol = 1))

  # cowplot::save_plot(filename = sprintf("%s/%s/aussie_oro_%s_scatterpie.svg",
  #                                       an_oro, plt_dir, nm),
  #                    plot = sct_plt1,
  #                    base_width = 12,
  #                    base_height = 9)
  cowplot::save_plot(filename = sprintf("~/Desktop/aussie_oro_%s_scatterpie.svg",
                                        nm),
                     plot = sct_plt1,
                     base_width = 12,
                     base_height = 9)

})
```

### Variable cell types
We can also take a look at the spatial scatterpie by looking at cell types which are not present throughout the entire tissue.
```{r}
lapply(names(st_ls), function(nm) {
  # Extract Seurat object
  se_st <- st_ls[[nm]]
  
  # Subset cell types from metadata
  metadata_subset <- se_st@meta.data[, paula_order]
  
  # Create masks
  keep_0.9 <- colSums(metadata_subset > 0) < 0.9 * ncol(se_st)
  keep_g0 <- colSums(metadata_subset > 0) > 0
  
  # Select cell types fullfiling the conditions
  ct_var <- colnames(metadata_subset)[keep_0.9 & keep_g0]

  sct_plt <- SPOTlight::scatterpie_plot(se_obj = se_st,
                                         cell_types_all = ct_var,
                                         pie_scale = 0.4) +
            scale_fill_manual(values = col_df[col_df$plt_name %in% ct_var, "ct_col"],
                              breaks = ct_var,
                              labels = stringr::str_wrap(string = ct_var,
                                                         width = 25)) +
            coord_fixed(ratio = 1) +
            theme(legend.position = "top",
                  legend.text = element_text(size = 12),
                  legend.title = element_blank()) +
            guides(fill = guide_legend(nrow = 3, byrow = TRUE))

  # cowplot::save_plot(filename = sprintf("%s/%s/aussie_oro_%s_scatterpie_subset.svg",
  #                                       an_oro, plt_dir, nm),
  #                    plot = sct_plt,
  #                    base_width = 12,
  #                    base_height = 9)
  cowplot::save_plot(filename = sprintf("~/Desktop/aussie_oro_%s_scatterpie_subset.svg",
                                        nm),
                     plot = sct_plt,
                     base_width = 9,
                     base_height = 9)

})
```

## Cell-Cell correlation plot
By looking at correlations we want to assess if there are cell types which are correlating in space. So when one is present is another one also present?

We will be using `ggcorrplot` to show these correlation plots a bit nicer:
http://www.sthda.com/english/wiki/ggcorrplot-visualization-of-a-correlation-matrix-using-ggplot2
<!-- http://www.sthda.com/english/wiki/visualize-correlation-matrix-using-correlogram -->

Get correlation matrix between all cell types
```{r}
# library(corrplot)
library(ggcorrplot)

# mat is a matrix object
cor.mtest <- function(mat, conf.level = 0.95){
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat <- lowCI.mat <- uppCI.mat <- matrix(NA, n, n)
    diag(p.mat) <- 0
    diag(lowCI.mat) <- diag(uppCI.mat) <- 1
    for(i in 1:(n-1)){
        for(j in (i+1):n){
            tmp <- cor.test(mat[,i], mat[,j], conf.level = conf.level)
            p.mat[i,j] <- p.mat[j,i] <- tmp$p.value
            lowCI.mat[i,j] <- lowCI.mat[j,i] <- tmp$conf.int[1]
            uppCI.mat[i,j] <- uppCI.mat[j,i] <- tmp$conf.int[2]
        }
    }
    return(list(p.mat, lowCI.mat, uppCI.mat))
}

lapply(names(st_ls), function(nm) {
  decon_df <- st_ls[[nm]]@meta.data %>%
    dplyr::select(all_of(paula_order))
  
  # Remove cell types not predicted to be on the tissue
  decon_df <- decon_df[, colSums(decon_df) > 0]
  decon_cor <- cor(decon_df)
  
  # Compute correlation P-value
  p.mat <- cor.mtest(decon_df, 0.95)
  colnames(decon_cor) <- stringr::str_wrap(string = colnames(decon_cor), width = 30)
  rownames(decon_cor) <- stringr::str_wrap(string = rownames(decon_cor), width = 30)
  
  cor_plt <- ggcorrplot::ggcorrplot(corr = decon_cor,
             p.mat = p.mat[[1]],
             hc.order = TRUE,
             type = "full",
             insig = "blank",
             lab = TRUE,
             outline.col = "lightgrey",
             method = "square",
             # colors = c("#4477AA", "white", "#BB4444"))
             colors = c("#6D9EC1", "white", "#E46726"),
             title = sprintf("Oropharyngeal cancer cell-cell proportion correlation\nSample - %s", nm),
             legend.title = "Correlation\n(Pearson)") +
     theme(
      plot.title = element_text(size = 22, hjust = 0.5, face = "bold"),
      legend.text = element_text(size = 12),
      legend.title = element_text(size = 15),
      axis.text.x = element_text(angle = 90),
      axis.text = element_text(size = 18, vjust = 0.5))
  cor_plt

  cowplot::save_plot(plot = cor_plt,
                   filename = sprintf("%s/%s/correlation_plot_oro_%s.svg",
                       an_oro, plt_dir, nm),
                   base_width = 16,
                   base_height = 12)
  
  # Now without labels
  cor_plt <- ggcorrplot::ggcorrplot(corr = decon_cor,
             p.mat = p.mat[[1]],
             hc.order = TRUE,
             type = "full",
             insig = "blank",
             lab = FALSE,
             outline.col = "lightgrey",
             method = "square",
             # colors = c("#4477AA", "white", "#BB4444"))
             colors = c("#6D9EC1", "white", "#E46726"),
             title = sprintf("Oropharyngeal cancer cell-cell proportion correlation\nSample - %s", nm),
             legend.title = "Correlation\n(Pearson)") +
    theme(
      plot.title = element_text(size = 25, hjust = 0.5, face = "bold"),
      legend.text = element_text(size = 18),
      legend.title = element_text(size = 22),
      axis.text.x = element_text(angle = 90, size = 18, vjust = 0.5),
      axis.text.y = element_text(vjust = 0.5, size = 18))
  
  cowplot::save_plot(plot = cor_plt,
                   filename = sprintf("%s/%s/correlation_plot_oro_%s_labeless.svg",
                       an_oro, plt_dir, nm),
                   base_width = 18,
                   base_height = 15)
})
```

### Correlation scatterplots
Select top 16 scatterplots pairs
```{r}
lapply(names(st_ls), function(nm) {
  decon_df <- st_ls[[nm]]@meta.data %>%
  dplyr::select(all_of(paula_order))
  # Remove cell types not predicted to be on the tissue
  decon_df <- decon_df[, colSums(decon_df) > 0]
  decon_cor <- cor(decon_df)

  decon_cor[lower.tri(decon_cor)] <- NA
  decon_low <- data.frame(decon_cor)
  colnames(decon_low) <- rownames(decon_low)
  
  ct_scatterplot <- decon_low %>%
    tibble::rownames_to_column("ct_1") %>% 
    tidyr::pivot_longer(cols = colnames(decon_cor),
                        names_to ="ct_2",
                        values_to = "cor_val") %>%
    dplyr::filter(ct_1 != ct_2) %>%
    dplyr::arrange(desc(abs(cor_val))) %>%
    head(16) %>%
    dplyr::mutate(ct_12 = sprintf("%s.%s", ct_1, ct_2)) %>%
    dplyr::pull(ct_12)
  
  corr_plts <- lapply(ct_scatterplot, function(i) {
    # separate ct_12
    str_ls <- stringr::str_split(i, "\\.")
    ct1 <-str_ls[[1]][[1]]
    ct2 <-str_ls[[1]][[2]]
    
    ggplot(decon_df,
           aes(x = decon_df[, ct1], y = decon_df[, ct2])) +
      geom_point() +
      ggpubr::stat_cor(method = "pearson",label.y = max(decon_df[, ct2]) + 0.05) +
      labs(x = stringr::str_wrap(sprintf("%s proportion", ct1), width = 30),
           y = stringr::str_wrap(sprintf("%s proportion", ct2), width = 30)) +
      theme_classic()
    }) %>%
    cowplot::plot_grid(plotlist = ., nrow = 4,ncol = 4)
  
  cowplot::save_plot(filename = sprintf("%s/%s/scater_cor_plot_oro_%s.svg",
                         an_oro, plt_dir, nm),
                     plot = corr_plts,
                     base_height = 12,
                     base_width = 16)
})
```

Now checking correlations of interest
```{r}
cor_int <- 
c("Recently activated CD4 T cells.Proliferative T cells",
  "Proliferative T cells.Proliferative monocytes and macrophages",
  "Regulatory T cells.Proliferative T cells",
  "Regulatory T cells.Terminally exhausted CD8 T cells",
  "Regulatory T cells.M2 TAMs",
  "B cells.Proliferative B cells")

lapply(names(st_ls), function(nm) {
  print(nm)
  # Extract metadata
  decon_df <- st_ls[[nm]]@meta.data %>%
    dplyr::select(all_of(paula_order))
  # Remove cell types not predicted to be on the tissue
  decon_df <- decon_df[, colSums(decon_df) > 0]
  decon_cor <- cor(decon_df)

  corr_plts <- lapply(cor_int, function(i) {
    # separate ct_12
    str_ls <- stringr::str_split(i, "\\.")
    ct1 <-str_ls[[1]][[1]]
    ct2 <-str_ls[[1]][[2]]
    
    ggplot(decon_df,
           aes(x = decon_df[, ct1], y = decon_df[, ct2])) +
      geom_point() +
      ggpubr::stat_cor(method = "pearson",
                       label.y = max(decon_df[, ct2]) + 0.05,
                       size = 5) +
      labs(x = stringr::str_wrap(sprintf("%s proportion", ct1), width = 30),
           y = stringr::str_wrap(sprintf("%s proportion", ct2), width = 30)) +
      theme_classic() +
      theme(
        axis.title = element_text(size = 20),
        axis.text = element_text(size = 14))
    }) %>%
    cowplot::plot_grid(plotlist = ., nrow = 3,ncol = 2)
  
  cowplot::save_plot(filename = sprintf("%s/%s/scater_cor_plot_oro_%s_int.svg",
                         an_oro, plt_dir, nm),
                     plot = corr_plts,
                     base_height = 16,
                     base_width = 12)
})

```

## Correlation CD73 and CD39 and Treg
Check assumptions
```{r}
lapply(c("Regulatory T cells", "Proliferative T cells", "Cytotoxic CD8 T cells"), function(ct) {
  # Shapiro-Wilk normality test for mpg
  print(shapiro.test(st_ls[[1]]@meta.data[, ct]))
  ggpubr::ggqqplot(st_ls[[1]]@meta.data[, ct])

})

lapply(c("ENTPD1", "NT5E"), function(gene) {
  # Shapiro-Wilk normality test for mpg
  print(shapiro.test(st_ls[[1]]@assays$SCT@data[gene, ]))
  ggpubr::ggqqplot(st_ls[[1]]@assays$SCT@sca[gene, ])

})
```

Regulatory T-cells inhibit the proliferation of effector T-cells by consuming and depleting IL-2 from the media and by releasing CD39 and CD73 which bind to the A2A receptor thus oinhibitng proliferation. ENTPD1 is the gene encoding for CD39 and NT5E encodes for CD73.
```{r}

library(ggpubr)
metadata <- dplyr::bind_cols(st_ls[[1]]@meta.data,
                             data.frame(t(st_ls[[1]]@assays$SCT@data[c("ENTPD1", "NT5E"), ])))

cor_plts <- lapply(c("Regulatory T cells", "Proliferative T cells", "Cytotoxic CD8 T cells"), function(ct) {
  tmp_ls <- lapply(c("ENTPD1", "NT5E"), function(gene) {
    
    tmp_plt <- ggpubr::ggscatter(data = metadata,
                      x = gene,
                      y = ct,
                      add = "reg.line") +
       ggpubr::stat_cor(method = "pearson")
    return(tmp_plt)
  })
  
  cowplot::plot_grid(plotlist = tmp_ls, ncol = 1)
})

cowplot::plot_grid(plotlist = cor_plts,
                   nrow = 1,
                   ncol = 3)
```

## Cell cycle
We can also look at cell cycling signature scores to see if some clusters are cycling more than others
```{r}
s.genes <- cc.genes.updated.2019$s.genes
g2m.genes <- cc.genes.updated.2019$g2m.genes

lapply(names(st_ls), function(nm) {
  print(nm)
  tmp <- Seurat::CellCycleScoring(st_ls[[nm]],
                                  s.features = s.genes,
                                  g2m.features = g2m.genes,
                                  set.ident = TRUE)
  
  # Visualization of cell cycle scores
  tmp <- Seurat::RunPCA(tmp, features = c(s.genes, g2m.genes))
  
  # Visualization 
  ## Phase
  umap_cc <- Seurat::DimPlot(object = tmp,
                             group.by = "Phase") +
    labs(title = "Cell cycle phase") +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 18))
  
  ## Cluster
  umap_clust <- Seurat::DimPlot(object = tmp,
                                group.by = "SCT_snn_res.0.1") +
    labs(title = "Stratification") +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 18))
  
  ## UMI count
  umap_umi <- Seurat::FeaturePlot(object = tmp,
                                  features = "nCount_Spatial") +
    labs(title = "UMI counts") +
    theme_void() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 18))
  
  # sp_cc <- Seurat::SpatialDimPlot(object = tmp,
  #                                 group.by = c("Phase")) +
  #   guides(fill = guide_legend(override.aes = list(size = 6))) +
  #   theme(
  #     legend.title = element_text(face = "bold"),
  #     legend.position = "top")
  
  cowplot::plot_grid(plotlist = list(umap_cc, umap_clust, umap_umi),
                     align = "hv",
                     axis = "trbl",
                     nrow = 1) %>%
    cowplot::save_plot(filename = sprintf("%s/%s/umap_hn_arr_%s.svg",
                                        an_oro, plt_dir, nm),
                       plot = .,
                       base_height = 5,
                       base_width = 15)

  # cowplot::save_plot(filename = sprintf("%s/%s/sp_cc_%s.svg",
  #                                       an_oro, plt_dir, nm),
  #                    plot = sp_cc,
  #                    base_height = 5,
  #                    base_width = 5)

})
```

## Clustering
```{r}
lapply(names(st_ls), function(nm) {
  
  # Spatial clustering
  sp_clust <- Seurat::SpatialDimPlot(object = st_ls[[nm]],
                                  group.by = "SCT_snn_res.0.1") +
    guides(fill = guide_legend(override.aes = list(size = 6))) +
    theme(
      legend.title = element_text(face = "bold"),
      legend.position = "top")
  
  cowplot::save_plot(filename = sprintf("%s/%s/sp_clust_%s.svg",
                                        an_oro, plt_dir, nm),
                     plot = sp_clust,
                     base_height = 5,
                     base_width = 5)
  
  # Spatial UMIs
  sp_umi <- Seurat::SpatialFeaturePlot(object = st_ls[[nm]],
                                       features = "nCount_Spatial") +
    guides(fill = guide_legend(override.aes = list(size = 6))) +
    labs(title = "UMI counts") +
    theme(
      legend.title =element_blank(),
      legend.position = "top",
      plot.title = element_text(hjust = 0.5, face = "bold", size = 18)) +
    scale_fill_gradient(low = "lightgrey", high = "blue")
  
  cowplot::save_plot(filename = sprintf("%s/%s/sp_umi_%s.svg",
                                        an_oro, plt_dir, nm),
                     plot = sp_umi,
                     base_height = 5,
                     base_width = 5)

})
```

## Session Info
```{r}
sessionInfo()
```

