---
title: "TICA_Projection_BrainMet_P12"
date: "`r format(Sys.time(), '%b %Y')`"
output:
  html_document:
    toc: yes
---

## Projection on BrainMet P12 (SKCM)

The following code generates the projection of cell types by TICA on a brain metastasis sample from a patient with melanoma. For this sample we have available both scRNA-seq and TCR sequencing to check the clonality associated on the cell types.

WARNING: due to huge size this script should be run on a computational cluster


### Load all necesary packages

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(Seurat)
library(magrittr)
library(pals)
library(flextable)
library(ComplexHeatmap)
library(patchwork)
library(matchSCore2)
library(RColorBrewer)
```

### Load a predefined color palette for each cell type

```{r palette, echo=FALSE}
values <- readRDS(file="~/aux/cell_type_palette.rds")
```

### Load TICA. Get the VariableFeatures

```{r load atlas}
atlas <- readRDS("~/aux/atlas_ds1000.rds") # load downsampled atlas
atlas <- subset(atlas, new_cell_types != "Mast cells") 
Idents(atlas) <- "new_cell_types"
atlas <- FindVariableFeatures(atlas, assay = "RNA", nfeatures = 5000) # 5000 Var.Feat for the RNA assay
```

### params$file contains the path to the Seurat object preprocessed with the TCR info on it. Basic preprocessing, normalization, scaling and dimensionality reduction was applied following Seurat's vignette (https://satijalab.org/seurat/v3.2/pbmc3k_tutorial.html).

```{r load query, echo=FALSE}
query <- readRDS(params$file) # load query dataset (BrainMet P12)
Idents(query) <- query$clusters
levels(query$clusters) <- c(1:length(unique(query$clusters))) # rename clusters from 1 to n
```

### We use FindTransferAnchors utility provided by Seurat (Stuart et al, 2019) for transfering cell type on TICA to the query object

```{r find anchors, echo=FALSE} 
anchors <- FindTransferAnchors(reference = atlas, # find anchors between query and atlas
                               query = query, 
                               dims = 1:30, 
                               normalization.method = "LogNormalize",
                               reference.assay = "RNA", 
                               query.assay = "RNA")
predictions <- TransferData(anchorset = anchors, refdata = atlas$new_cell_types, dims = 1:30) # transfer new_cell_types annot
query <- AddMetaData(query, metadata = predictions) # add to object metdata
``` 

### Show the results of the projection as a table

```{r table, results = "markup", echo=FALSE}
tab <- as.data.frame.matrix(table(query$predicted.id, Idents(query))) # create table
tab$annotated_cell_type <- rownames(tab)

flextable(tab) %>% 
  set_header_labels(annotated_cell_type = " ") %>% 
  autofit() %>% 
  theme_vanilla() %>% 
  set_caption(paste0(toString(dim(query)[2]), " cells total"))  %>% # add number of total cells at the top
  align(align = "center", part = "all")
```

### Plot the TICA predictions and their associated clonal size

```{r plots, results = "markup", fig.height=10, fig.width=12, echo=FALSE}
# plot umap colored by original cell type, predicted cell type and clusters
query$cell_type <- Idents(query)
p1 <- DimPlot(query, group.by = "cell_type", pt.size = 1) +
  NoAxes()
p1 + ggtitle("Predicted celltype") 

query$umap1 <- query@reductions$umap@cell.embeddings[,1]
query$umap2 <- query@reductions$umap@cell.embeddings[,2]
aux_df <- as.data.frame(cbind(query$umap1,query$umap2,Idents(query),query$Clono_size))
colnames(aux_df) <- c("umap1","umap2","clusters","Clono_size")
aux_df$umap1 <- as.numeric(as.character(aux_df$umap1))
aux_df$umap2 <- as.numeric(as.character(aux_df$umap2))
aux_df$clusters <- as.character(aux_df$clusters)

p2 <- ggplot(aux_df, aes(x=umap1, y=umap2)) + geom_point(aes(color=Clono_size),size = 1.4) + ggtitle("Clono_size") +
  scale_colour_gradient(low = "grey", high = "darkgreen") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  NoAxes()
p2
```

